\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.85in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}

\hypersetup{colorlinks=true, linkcolor=blue!60!black, urlcolor=blue!60!black}
\setlist[itemize]{leftmargin=1.2em,itemsep=2pt,topsep=3pt}
\setlength{\parskip}{5pt}
\setlength{\parindent}{0pt}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\est}{\emph{estimate}}
\newcommand{\obs}{\emph{observed}}

\title{\textbf{Replication Resource Assessment and 1000-Paper Scaling Projection}\\
\large REPLICATE Project}
\author{Prepared from the REPLICATE-PROJECT reports}
\date{April 2026}

\begin{document}
\maketitle

\begin{abstract}
This document summarizes the time, compute resources, software stack, tool challenges, and scaling implications observed in the REPLICATE-PROJECT corpus. The project contains completed and partial replications across mathematical theory, machine learning, physics simulation, computational chemistry, bioinformatics, materials modeling, astrophysics, and engineering. The tables below distinguish directly observed values from estimates. The final sections project the resources required to replicate 1000 computational papers and estimate the expansion factor required to move from replication to original scientific work.
\end{abstract}

\section{Executive Summary}

The completed reports show that AI-assisted replication is practical for a large fraction of computational papers, but the required resources vary by more than six orders of magnitude. Mathematical, algorithmic, and small-data machine-learning replications often complete in seconds to hours on a workstation. Simulation-heavy work, GPU deep learning, molecular dynamics, combustion, DFT, and cosmological simulations require GPU clusters, licensed software, or large HPC allocations. The main limiter is not usually writing code; it is recovering the missing operational details: exact datasets, software versions, random seeds, model hyperparameters, licensed solvers, preprocessing pipelines, and production-scale compute.

For a 1000-paper program, a realistic mixed portfolio requires a triage pipeline. A broad replication program should not assume uniform full-fidelity replication. Instead, papers should be divided into mathematical/algorithmic, workstation computational, GPU/HPC tractable, and frontier/HPC-original-scale categories. A balanced 1000-paper replication effort would likely require roughly 20--40 staff-years of technical labor, 0.5--3 million GPU-hours or equivalent for the compute-heavy subset, and a dedicated software/data operations function. Full production-level replication of all papers, including the original compute scale, could be an order of magnitude larger.

\section{Scope and Method}

The estimates in this document are based on local report files under \code{REPLICATE-PROJECT}, especially completed replication reports, status files, and \code{COMPUTATIONAL\_TOOLS\_INVENTORY.md}. Values labeled \obs{} are reported directly in the replication documents. Values labeled \est{} are extrapolations from observed runs, reported blockers, and common practice for the relevant scientific domain.

\section{Observed Replication Time and Resource Classes}

\begin{longtable}{p{3.0cm}p{3.6cm}p{2.4cm}p{2.8cm}p{4.4cm}}
\toprule
\textbf{Class} & \textbf{Examples from project} & \textbf{Human time per paper} & \textbf{Compute per paper} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Class} & \textbf{Examples from project} & \textbf{Human time per paper} & \textbf{Compute per paper} & \textbf{Notes} \\
\midrule
\endhead
Mathematical / definitional & GraphBLAS, Hausdorff integer sequences, Rice--Mele shift vector, chiral spin order & 0.5--2 days \est{} & Seconds to minutes CPU & Best fit for AI-assisted replication. Success depends on equations being complete and testable. \\
\addlinespace
Small algorithmic / numerical & CPW analytical model, photo-z PDFs, FDTD reduced cases, qZSI common-mode voltage & 1--3 days \est{} & 30 seconds to 1 hour CPU; occasional 0.5--2 GB RAM & Typically reproducible with Python/NumPy/SciPy. Full commercial simulations may still be out of scope. \\
\addlinespace
Machine learning, reduced scale & STEM segmentation surrogate, Graph RL restoration, Bayesian optimization, latent SDE reduced model, hybrid CHF surrogate & 2--7 days \est{} & Minutes to hours CPU/GPU & Often requires surrogate data because original training data are missing or too large. Exact reproduction is limited by data and hyperparameter ambiguity. \\
\addlinespace
GPU deep learning / generative AI & PVMol-Gen, neural VMC, chaotic neural ODE & 1--3 weeks \est{} & Minutes to tens of GPU-hours for reduced runs; tens to hundreds for full runs & Environment setup, model instability, and data reconstruction dominate effort. \\
\addlinespace
Computational chemistry / materials & Pt/La$_2$Ti$_2$O$_7$ DFT, 2D GaN, perovskite molecule discovery & 1--4 weeks \est{} & Tens to thousands of GPU/CPU-hours & Exact replication depends on pseudopotentials, exchange-correlation functional, k-mesh, relaxation criteria, slab models, and licensed or specialized codes. \\
\addlinespace
Bioinformatics pipelines & Virophage taxonomy, metagenome binning, protein clustering & 3 days--3 weeks \est{} & Hours to days CPU; 10s--100s GB storage for full datasets & Toolchains are broad and brittle. Reference databases, version drift, and network/database access are the main risks. \\
\addlinespace
Molecular dynamics / Markov models & MSM/OOM alanine dipeptide, VMC, protein/trajectory analyses & 1--4 weeks \est{} & Observed MSM: about 2 h short trajectories + 4 h long reference on 8 A100s; analysis $<$5 min & Reproducibility depends on force fields, initial states, trajectory length, thermostat/barostat, and random seeds. \\
\addlinespace
Large-scale PDE / combustion / cosmology & Ignition kernel, cosmic reionization, full non-Markovian FDTD, production turbulent flow & 1--3 months \est{} & $10^4$--$10^6$ CPU-hours or 10s--1000s GPU-hours & Simplified replication is possible; full-fidelity replication requires production HPC workflows. \\
\bottomrule
\caption{Observed and estimated resource classes for papers in the REPLICATE corpus.}
\end{longtable}

\section{Representative Report-Level Resource Notes}

\begin{landscape}
\begin{longtable}{p{4.2cm}p{2.7cm}p{3.5cm}p{3.5cm}p{6.0cm}}
\toprule
\textbf{Replication report} & \textbf{Status} & \textbf{Observed compute} & \textbf{Observed / implied human effort} & \textbf{Primary limitation} \\
\midrule
\endfirsthead
\toprule
\textbf{Replication report} & \textbf{Status} & \textbf{Observed compute} & \textbf{Observed / implied human effort} & \textbf{Primary limitation} \\
\midrule
\endhead
GraphBLAS mathematical foundations & Fully confirmed & Test suite $<$1 s CPU & 1--2 days \est{} & Mainly implementation discipline; paper is definitional and internally testable. \\
\addlinespace
Photo-z PDF compression & Confirmed & 54 s CPU \obs{} & 1--2 days \est{} & Original BPZ mock catalogs unavailable; synthetic GMM catalogs used. \\
\addlinespace
CPW resonator mask & Substantially confirmed & 27 s total CPU; sparse solve 2.5 s \obs{} & 1--3 days \est{} & Full 3D FEM / HFSS-style analysis not reproduced. \\
\addlinespace
FDTD delay PDE & Substantially confirmed & 266 s + 52 s + 44 s CPU for reported reduced cases \obs{} & 2--4 days \est{} & Full non-Markovian case estimated at 50--125 GB memory. \\
\addlinespace
Bayesian optimization qHSRI & Partially confirmed & About 42 min CPU \obs{} & 3--5 days \est{} & Different implementation stack; omitted noisy/multi-objective/application cases. \\
\addlinespace
Chiral spin order & Strong qualitative confirmation & $<$10 s CPU \obs{} & 1--2 days \est{} & Mean-field theory replicated; beyond-mean-field critical exponent not captured. \\
\addlinespace
Trapped-ion light scattering & Core analytic result confirmed & Small ODE tests CPU; all tests pass \obs{} & 3--5 days \est{} & Quantitative figures require Penning-trap mode simulation details not fully specified. \\
\addlinespace
STEM deep learning segmentation & Substantial reduced replication & 95 s on one A100 80 GB \obs{} & 3--7 days \est{} & Synthetic images replace experimental/multislice image stacks. \\
\addlinespace
PVMol-Gen & Partially confirmed & 8 A100s for SELFIES pipeline; generation about 8.5 h for a major stage \obs{} & 1--3 weeks \est{} & Stage 1 classifier below paper metric; DFT/xTB filters and SMILES-X details are major uncertainties. \\
\addlinespace
Neural VMC for light nuclei & Partial method confirmation & Single A100 40 GB; total wall time $<$150 s for reported runs \obs{} & 3--7 days \est{} & Simpler Minnesota interaction used instead of full AV6'/AV8' operator structure. \\
\addlinespace
MSM/OOM bias correction & Strong confirmation & 8 A100 80 GB; short ensemble about 2 h, long reference about 4 h, analysis $<$5 min \obs{} & 1--2 weeks \est{} & Exact reference trajectories and MD settings drive reproducibility. \\
\addlinespace
Latent SDE quasar variability & Reduced method replication & 160 s CPU vs paper about 6 weeks on V100 \obs{} & 3--7 days \est{} & Full six-band LSST-like data generation and GPU-scale training not reproduced. \\
\addlinespace
Hybrid CHF ML & Partial confirmation & About 7 min on 8-core CPU \obs{} & 3--5 days \est{} & NRC CHF database not redistributable; synthetic surrogate used. \\
\addlinespace
Cosmic reionization on computers & Semi-analytic replication & About 3 min CPU, $<$2 GB RAM \obs{} & 3--7 days \est{} & Original CROC simulations require about $10^4$ cores and months; surrogate FGPA model used. \\
\addlinespace
Ignition kernel turbulent combustion & Simplified attempt failed key trend; GPU framework partial & Original about 40,000 CPU-h per case, 20 cases about 800,000 CPU-h \obs{}; GPU estimate about 80 A100 GPU-h for full open-source run \est{} & 1--3 months \est{} & Requires compressible reacting LES with detailed chemistry; low-Mach solver was physically mismatched. \\
\bottomrule
\caption{Representative resource notes extracted from the reports.}
\end{longtable}
\end{landscape}

\section{Comprehensive Tool and Software Inventory}

\begin{longtable}{p{3.2cm}p{4.2cm}p{5.1cm}p{4.0cm}}
\toprule
\textbf{Category} & \textbf{Tools} & \textbf{Replication role} & \textbf{Challenges} \\
\midrule
\endfirsthead
\toprule
\textbf{Category} & \textbf{Tools} & \textbf{Replication role} & \textbf{Challenges} \\
\midrule
\endhead
Core scientific Python & Python, NumPy, SciPy, pandas, matplotlib, h5py, xarray, netCDF tools & Most numerical analysis, plotting, data processing, reduced physics models & Version drift, binary wheels on unusual architectures, silent numerical differences. \\
\addlinespace
Testing / workflow & pytest, shell scripts, Make, LaTeX, Jupyter notebooks & Regression tests, figure generation, reproducible reports & Notebooks often lack deterministic execution; scripts need dependency pinning. \\
\addlinespace
Machine learning & PyTorch, TensorFlow, Keras, scikit-learn, GPyTorch, BoTorch, TensorFlow Probability, Ray Tune & Deep learning, Bayesian optimization, uncertainty models, neural ODE/SDE models & GPU/CUDA compatibility, nondeterminism, hyperparameter ambiguity, deprecated APIs. \\
\addlinespace
Generative AI / language models & Hugging Face Transformers, GPT-2, LLaMA-2, RoBERTa/SciBERT, BERTopic, HDBSCAN, UMAP & Molecular generation, domain language models, embeddings and clustering & Model weights, tokenizer variants, GPU memory, licensing, exact pretraining corpora unavailable. \\
\addlinespace
Cheminformatics & RDKit, SMILES-X, SELFIES, PubChem API, PAINS/SA filters, Morgan fingerprints & Molecular classification, generation, filtering, clustering & SMILES-X reproducibility gap, API dependence, molecular standardization differences, missing DFT/xTB filters. \\
\addlinespace
DFT / electronic structure & Quantum ESPRESSO, VASP, PBE/PBE0, PAW/SSSP pseudopotentials, Bader analysis, VESTA & Materials band structures, DOS/PDOS, adsorption and slab calculations & VASP license; QE GPU build quirks; pseudopotential and smearing choices change results. \\
\addlinespace
Molecular dynamics & OpenMM, AMBER ff14SB/TIP3P, ACEMD, LAMMPS, EAM potentials, OVITO/Voronoi analysis & Trajectory generation, Markov state models, materials deformation & Long trajectories, force-field versioning, initial conditions, thermostat/barostat choices. \\
\addlinespace
Combustion / fluid dynamics & PeleC, PeleLMeX, AMReX, SUNDIALS/CVODE, DRM19 chemistry, CharLES$^X$ reference & Reacting-flow LES and ignition-kernel dynamics & Proprietary original solver; low-Mach vs compressible physics mismatch; stiff chemistry and GPU runtime failures. \\
\addlinespace
Nuclear / reactor physics & SCALE 6.3, ORIGEN, TRITON, KENO-VI, NEWT, Serpent, ENDF/B data & Depletion and neutron transport studies & Licenses/distribution controls, nuclear data library versions, high compute cost. \\
\addlinespace
Electromagnetic / circuit simulation & Ansys HFSS, COMSOL, Palace, MATLAB/Simulink, PySpice/ngspice & CPW resonators, qZSI common-mode voltage, FEM/eigenmode simulations & Commercial licenses; geometry/mesh details underspecified; open-source approximations often lower fidelity. \\
\addlinespace
Bioinformatics & HMMER/hmmsearch, BLAST+, DIAMOND, MAFFT, MUSCLE, IQ-TREE, clipkit, Prodigal, MCL, InfoMap, MUMmer, CheckV, metaSPAdes, MetaBAT2, minimap2, samtools & Taxonomy, genome binning, alignments, phylogenies, metagenomic assembly & Large databases, version sensitivity, long install chains, network/download brittleness. \\
\addlinespace
R ecosystem & R, hetGP, DiceOptim, GPareto, DiceKriging, mlrMBO, mco, pso, fldgen, ggplot2, dplyr, tidyr, ggtree & Bayesian optimization, climate emulation, plotting, phylogenetics & Some packages are old or R-only; reproducing R results in Python can alter rankings. \\
\addlinespace
Parallel / HPC & MPI, OpenMP, POSIX threads, CUDA, OpenCL, multiprocessing, SLURM/PBS & Scaling experiments, GPU training, trajectory generation, CFD/DFT/MD & Queue delays, module incompatibilities, GPU driver failures, hardware-specific performance. \\
\addlinespace
Databases / external data & OEIS, NCBI GenBank/RefSeq/nr, IMG/VR, Pfam, PDB70, PubChem, IRPhEP, ENDF/B, experimental proprietary databases & Inputs, benchmarks, labels, reference datasets & Access restrictions, nonredistributable data, changing database snapshots. \\
\bottomrule
\caption{Software and tool inventory with recurring replication challenges.}
\end{longtable}

\section{Common Replication Challenges}

\begin{longtable}{p{3.5cm}p{6.5cm}p{6.0cm}}
\toprule
\textbf{Challenge} & \textbf{Observed impact} & \textbf{Mitigation for a scaled program} \\
\midrule
\endfirsthead
\toprule
\textbf{Challenge} & \textbf{Observed impact} & \textbf{Mitigation for a scaled program} \\
\midrule
\endhead
Missing datasets & Several reports used synthetic surrogates because original catalogs, experimental databases, or simulation outputs were unavailable. & Data acquisition team; DOI/dataset tracking; institutional agreements; snapshot mirrors. \\
\addlinespace
Licensed / proprietary software & VASP, SCALE, MATLAB/Simulink, HFSS/COMSOL, CharLES$^X$ block exact reproduction. & Maintain licensed software pool; define acceptable open-source substitute criteria; record fidelity level. \\
\addlinespace
Underspecified parameters & Pseudopotentials, random seeds, trap modes, mesh settings, optimizer settings, and filtering thresholds often missing. & Standard replication metadata checklist; structured uncertainty log; sensitivity analysis. \\
\addlinespace
Version drift & Old Python/R APIs, GPU builds, CUDA compatibility, pandas changes, and binary package issues caused failures. & Container registry; lockfiles; reproducible build recipes; long-term artifact archive. \\
\addlinespace
Compute mismatch & Full-fidelity combustion, cosmology, DFT, and MD can be orders of magnitude larger than reduced replication. & Tiered replication: reduced, comparable, and production-fidelity levels. \\
\addlinespace
Benchmark ambiguity & Some papers report figures without exact numeric data or use private baselines. & Digitization plus uncertainty bands; ask authors when possible; report qualitative/quantitative status separately. \\
\addlinespace
Non-determinism & ML and stochastic simulations vary with seed, hardware, libraries, and thread count. & Multi-seed protocols; confidence intervals; deterministic flags where possible. \\
\addlinespace
Toolchain breadth & Bioinformatics and HPC workflows require many tools, databases, and build systems. & Domain-specific environment templates; staff specialists by domain; automated smoke tests. \\
\bottomrule
\caption{Recurring replication challenges and mitigation strategies.}
\end{longtable}

\section{Projection for Replicating 1000 Papers}

\subsection{Portfolio Assumption}

A plausible 1000-paper replication portfolio will be heterogeneous. The following projection assumes a mix similar to the REPLICATE corpus after triage toward computationally tractable papers.

\begin{longtable}{p{4.0cm}r r r r}
\toprule
\textbf{Paper class} & \textbf{Share} & \textbf{Count} & \textbf{Staff-days / paper} & \textbf{Compute / paper} \\
\midrule
\endfirsthead
\toprule
\textbf{Paper class} & \textbf{Share} & \textbf{Count} & \textbf{Staff-days / paper} & \textbf{Compute / paper} \\
\midrule
\endhead
Mathematical / algorithmic & 25\% & 250 & 1--2 & $<$1 CPU-hour \\
Workstation numerical / small ML & 35\% & 350 & 2--5 & 1--100 CPU-hours \\
GPU ML / medium simulation & 20\% & 200 & 5--15 & 1--200 GPU-hours \\
Domain pipelines / databases & 10\% & 100 & 7--20 & 100--5,000 CPU-hours plus storage \\
Heavy HPC / full simulation & 10\% & 100 & 15--60 & $10^4$--$10^6$ CPU-hours or 100--5,000 GPU-hours \\
\bottomrule
\caption{Assumed 1000-paper mix after computational-replicability triage.}
\end{longtable}

\subsection{Aggregate Resource Estimate}

\begin{longtable}{p{4.4cm}p{3.4cm}p{3.4cm}p{5.0cm}}
\toprule
\textbf{Program level} & \textbf{Human labor} & \textbf{Compute} & \textbf{Interpretation} \\
\midrule
\endfirsthead
\toprule
\textbf{Program level} & \textbf{Human labor} & \textbf{Compute} & \textbf{Interpretation} \\
\midrule
\endhead
Screening only & 1--3 staff-years & Small workstation cluster & Identify replicability, software stack, data availability, and likely cost for 1000 papers. \\
\addlinespace
Reduced replication & 20--40 staff-years & 0.1--0.5 million GPU-hour equivalent; 1--10 million CPU-hours & Rebuild core claims with reduced data, surrogate datasets, and lower-fidelity simulations where needed. \\
\addlinespace
Comparable-fidelity replication & 50--100 staff-years & 0.5--3 million GPU-hour equivalent; 10--100 million CPU-hours & Aim to reproduce most figures/tables at comparable scale where data/software are accessible. \\
\addlinespace
Production-fidelity replication & 100--250 staff-years & 3--20 million GPU-hour equivalent; 0.1--1 billion CPU-hours & Full original-scale reproduction, including large PDE, MD, DFT, cosmology, and combustion runs. \\
\bottomrule
\caption{Aggregate 1000-paper replication program estimate. One staff-year is approximated as 220 working days.}
\end{longtable}

\subsection{Staffing Model}

\begin{longtable}{p{4.0cm}p{3.0cm}p{8.0cm}}
\toprule
\textbf{Role} & \textbf{Headcount for 1000-paper reduced/comparable program} & \textbf{Responsibilities} \\
\midrule
\endfirsthead
\toprule
\textbf{Role} & \textbf{Headcount for 1000-paper reduced/comparable program} & \textbf{Responsibilities} \\
\midrule
\endhead
Replication scientists / research software engineers & 12--25 & Paper triage, implementation, tests, figure generation, documentation. \\
Domain specialists & 5--12 & DFT, bioinformatics, ML, physics simulation, MD, nuclear, combustion, astrophysics review. \\
HPC / DevOps engineers & 3--6 & Cluster jobs, containers, CUDA/MPI builds, storage, CI, artifact archiving. \\
Data acquisition / curation & 2--5 & Dataset recovery, database snapshots, licensing, metadata. \\
Technical editors / QA reviewers & 2--4 & Report normalization, evidence grading, audit trail, reproducibility checklists. \\
Program lead / project management & 1--3 & Prioritization, scheduling, risk management, author outreach. \\
\bottomrule
\caption{Indicative staffing for a 2--3 year 1000-paper effort.}
\end{longtable}

\section{Expansion from Replication to Original Work}

Original work is not just ``more replication.'' It adds hypothesis generation, experimental design, parameter exploration, validation against new data, uncertainty quantification, writing, and peer-review response. The expansion factor depends strongly on domain.

\begin{longtable}{p{3.7cm}p{3.0cm}p{3.0cm}p{6.0cm}}
\toprule
\textbf{Domain / work type} & \textbf{Replication baseline} & \textbf{Original-work multiplier} & \textbf{Why original work expands} \\
\midrule
\endfirsthead
\toprule
\textbf{Domain / work type} & \textbf{Replication baseline} & \textbf{Original-work multiplier} & \textbf{Why original work expands} \\
\midrule
\endhead
Mathematical / algorithmic & 1--2 days & 3--10$\times$ & Need new theorem/algorithm, proof search, counterexamples, broader test cases, and exposition. \\
\addlinespace
Small numerical method & 2--5 days & 5--15$\times$ & Need parameter sweeps, ablations, robustness tests, and comparison against alternatives. \\
\addlinespace
Machine learning & 1--2 weeks & 5--20$\times$ & Need dataset construction, model selection, tuning, multi-seed evaluation, baselines, and generalization tests. \\
\addlinespace
DFT/materials & 1--4 weeks & 10--50$\times$ & Need structure search, multiple surfaces/defects, convergence studies, adsorption pathways, higher-level validation. \\
\addlinespace
MD / molecular simulation & 1--4 weeks & 10--50$\times$ & Need longer sampling, force-field validation, multiple systems, uncertainty quantification. \\
\addlinespace
Bioinformatics & 1--3 weeks & 5--25$\times$ & Need new database curation, biological validation, phylogenetic sensitivity, manual annotation. \\
\addlinespace
Combustion / large PDE / climate / cosmology & 1--3 months & 10--100$\times$ & Need production simulations, ensemble runs, mesh/time-step convergence, validation data, and large-scale analysis. \\
\bottomrule
\caption{Estimated expansion factor from replication to original work.}
\end{longtable}

\subsection{1000-Paper Equivalent Original-Work Projection}

If the same topical distribution were used not for replication but for producing original publishable contributions, the total effort would likely expand by a factor of 8--30 for a conservative program and 30--100 for frontier simulation-heavy work. A 1000-paper reduced/comparable replication effort estimated at 20--100 staff-years therefore maps roughly to:

\begin{longtable}{p{4.2cm}p{3.5cm}p{3.5cm}p{5.0cm}}
\toprule
\textbf{Original-work ambition} & \textbf{Staff-years} & \textbf{Compute multiplier} & \textbf{Likely output} \\
\midrule
\endfirsthead
\toprule
\textbf{Original-work ambition} & \textbf{Staff-years} & \textbf{Compute multiplier} & \textbf{Likely output} \\
\midrule
\endhead
Incremental extensions & 150--400 & 3--10$\times$ & Add ablations, variants, new baselines, modest parameter sweeps, or additional datasets. \\
\addlinespace
New publishable studies & 300--1500 & 10--50$\times$ & Produce robust new results in selected domains, with peer-review-grade validation. \\
\addlinespace
Frontier original science at scale & 1000+ & 50--200$\times$ for heavy subsets & New large simulations, new datasets, experimental campaigns, or production HPC campaigns. \\
\bottomrule
\caption{Approximate expansion from a 1000-paper replication program to original research programs.}
\end{longtable}

\section{Operational Recommendations}

\begin{enumerate}
\item Use a three-tier evidence label for every paper: \textbf{reduced replication}, \textbf{comparable-fidelity replication}, and \textbf{production-fidelity replication}. This prevents a fast surrogate from being mistaken for exact reproduction.
\item Build a reusable software environment library organized by domain: Python ML, R optimization, bioinformatics, DFT, MD, combustion, nuclear, and LaTeX/reporting.
\item Require every replication to produce: executable scripts, dependency lockfile or container recipe, output checksums, key figures/tables, test suite when possible, and a structured limitations table.
\item Maintain a central data registry with dataset status: public, mirrored, author-provided, licensed, nonredistributable, synthetic substitute, or missing.
\item Reserve HPC for papers that pass a low-cost pilot. Many core claims can be tested with a reduced model before committing thousands of GPU-hours.
\item Separate engineering success from scientific success. A software pipeline may run correctly while failing to reproduce the original claim because of missing data, inappropriate surrogate physics, or underspecified parameters.
\end{enumerate}

\section{Bottom Line}

The REPLICATE corpus supports a practical conclusion: AI-assisted replication can make 1000-paper computational replication plausible, but only with triage, evidence grading, domain specialists, and serious environment/data management. The median paper is manageable on workstation or modest GPU resources. The tail dominates cost: a small number of combustion, cosmology, DFT, MD, and large-model papers can consume most compute and staff time. Original work expands the resource envelope substantially, usually by one order of magnitude and sometimes by two, because it requires exploration rather than reconstruction.

\end{document}
