\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{array}
\usepackage{enumitem}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}

\title{PDE Corpus — Final 100 Ranked Papers\\
\large Stage 4: Deep-Read \& Reproduction Feasibility Assessment}
\author{REPLICATE-PROJECT, Stage 4}
\date{\today}

\begin{document}
\maketitle

\section{Motivation \& Methodology}

This report summarises the final 100 papers selected from the PDE-numerical-methods corpus
(\textasciitilde17{,}000 candidates) for potential reproduction by the REPLICATE project's PDE-solver
AI agents. The pipeline was:

\begin{enumerate}[nosep]
  \item \textbf{Stage 1} — Raw corpus assembly from 7 preselected domains (Poisson,
        heat, Burgers, Helmholtz, Navier--Stokes, etc.), $\approx$17{,}000 entries.
  \item \textbf{Stage 2} — Initial heuristic scoring + top-300 shortlist.
  \item \textbf{Stage 3} — Semantic Scholar enrichment (citations, venue, OA PDF URLs),
        domain rebalancing, top-100 shortlist.
  \item \textbf{Stage 4 (this report)} — OA PDF fetch (70/100 successful),
        per-paper signal extraction (code repos, test problems, numerical methods,
        convergence tables), reproducibility/interest scoring, domain-balanced
        final ranking, reproduction-plan scaffolding.
\end{enumerate}

\subsection{Scoring Rubric}

\textbf{Reproducibility (1--10)} combines: availability of full PDF; concrete numerical
methods (FEM/FVM/FDM/DG/spectral/PINN); public code (GitHub, Zenodo, CodeOcean);
compatibility with open-source stacks (FEniCS, PETSc, deal.II, OpenFOAM, Clawpack,
JAX, Julia DifferentialEquations.jl); presence of convergence tables or benchmark
problems; compute feasibility ($< 12$\,h on available GPU/CPU resources).

\textbf{Interest (1--10)} weights: citation count, recency, methodological novelty,
active research direction (ML-for-PDE, quantum algorithms), benchmark utility.

\textbf{Priority:} \emph{A} = ready to go (repro $\ge 8$ and interest $\ge 7$);
\emph{B} = modest gaps (repro $\ge 6$ and interest $\ge 5$); \emph{C} = hard.

\subsection{Enrichment Statistics}

\begin{itemize}[nosep]
  \item PDFs successfully downloaded: \textbf{70/100}
    (30 fell back to abstract-only due to paywall / 403).
  \item Topic buckets covered: \textbf{16}.
  \item Priority distribution: \textbf{A=14, B=45, C=41}.
\end{itemize}

\section{Domain Breakdown}

\begin{center}
\begin{tabular}{lr}
\toprule
\textbf{Topic bucket} & \textbf{Count} \\
\midrule
Fluid/NavierStokes & 24 \\
Elliptic & 17 \\
NonlinearScalar & 14 \\
ML-operator/PINN & 9 \\
Heat/Diffusion & 9 \\
Helmholtz/Wave & 5 \\
Hyperbolic & 4 \\
Stochastic & 4 \\
Quantum/Kinetic & 4 \\
PhaseField/RD & 3 \\
AMR/Multigrid & 2 \\
Relativity/GR & 1 \\
Fractional & 1 \\
Other & 1 \\
FreeBoundary & 1 \\
Porous/Darcy & 1 \\
\bottomrule
\end{tabular}
\end{center}

\section{Top 10 — Detailed Summaries}

\subsection*{\#1 — Can physics-informed neural networks beat the finite element method?}
\textbf{Score:} 19 \quad \textbf{Priority:} A \quad \textbf{Topic:} ML-operator/PINN \quad \textbf{Year:} 2023 \quad \textbf{Cites:} 188

\textit{Authors:} T. G. Grossmann;U. J. Komorowska;J. Latz;C. Schönlieb \\ 
\textit{DOI:} \url{https://doi.org/10.1093/imamat/hxae011} \\ 
\textbf{Reproducibility } (10/10): full-pdf-available; github:github.com/TamaraGrossmann/FEM-vs-PINNs.; methods:finite element,finite difference,finite volume,spectral; tools:fenics,julia,jax; tests:heat equation,poisson,navier-stokes; conv-table \\ 
\textbf{Interest } (9/10): cited:188; recent; active-ml-qc; good-benchmark \\ 
\textbf{Core method:} finite element \\ 
\textbf{Test problems:} heat equation, poisson, navier-stokes \\ 
\textbf{Tools:} PyTorch or JAX \\ 
\textbf{Est. effort:} 4h, GPU=True \\ 

\subsection*{\#2 — Solving High-Dimensional PDEs with Latent Spectral Models}
\textbf{Score:} 18 \quad \textbf{Priority:} A \quad \textbf{Topic:} ML-operator/PINN \quad \textbf{Year:} 2023 \quad \textbf{Cites:} 95

\textit{Authors:} Haixu Wu;Tengge Hu;Huakun Luo;Jianmin Wang;Mingsheng Long \\ 
\textit{DOI:} \url{https://doi.org/10.48550/arXiv.2301.12664} \\ 
\textbf{Reproducibility } (10/10): full-pdf-available; github:github.com/thuml/Latent-; methods:finite element,spectral,pseudospectral,pinn; tools:pytorch; tests:navier-stokes,darcy,diffusion; conv-table \\ 
\textbf{Interest } (8/10): modest-cite:95; recent; active-ml-qc; good-benchmark \\ 
\textbf{Core method:} finite element \\ 
\textbf{Test problems:} navier-stokes, darcy, diffusion \\ 
\textbf{Tools:} PyTorch or JAX \\ 
\textbf{Est. effort:} 4h, GPU=True \\ 

\subsection*{\#3 — Koopman neural operator as a mesh-free solver of non-linear partial differential equations}
\textbf{Score:} 18 \quad \textbf{Priority:} A \quad \textbf{Topic:} ML-operator/PINN \quad \textbf{Year:} 2023 \quad \textbf{Cites:} 74

\textit{Authors:} Wei Xiong;Xiaomeng Huang;Ziyang Zhang;Ruixuan Deng;Pei Sun;Yang Tian \\ 
\textit{DOI:} \url{https://doi.org/10.48550/arXiv.2301.10022} \\ 
\textbf{Reproducibility } (10/10): full-pdf-available; github:github.com/Koopman-Laboratory/; methods:finite element,finite difference,spectral,krylov; tools:pytorch; tests:burgers,navier-stokes,stokes; conv-table \\ 
\textbf{Interest } (8/10): modest-cite:74; recent; active-ml-qc; good-benchmark \\ 
\textbf{Core method:} finite element \\ 
\textbf{Test problems:} burgers, navier-stokes, stokes \\ 
\textbf{Tools:} PyTorch or JAX \\ 
\textbf{Est. effort:} 4h, GPU=True \\ 

\subsection*{\#4 — Lifex-cfd: an Open-source Computational Fluid Dynamics Solver for Cardiovascular Applications}
\textbf{Score:} 18 \quad \textbf{Priority:} A \quad \textbf{Topic:} Fluid/NavierStokes \quad \textbf{Year:} 2023 \quad \textbf{Cites:} 61

\textit{Authors:} P. C. Africa;Ivan Fumagalli;M. Bucelli;Alberto Zingaro;L. Dede’;A. Quarteroni \\ 
\textit{DOI:} \url{https://doi.org/10.48550/arXiv.2304.12032} \\ 
\textbf{Reproducibility } (10/10): full-pdf-available; github:github.com/nschloe/meshio; methods:finite element,discontinuous galerkin,bdf,multigrid; tools:fenics,petsc,deal.ii; tests:poisson,navier-stokes,advection; conv-table \\ 
\textbf{Interest } (8/10): modest-cite:61; recent; good-benchmark \\ 
\textbf{Core method:} finite element \\ 
\textbf{Test problems:} poisson, navier-stokes, advection \\ 
\textbf{Tools:} FEniCS, OpenFOAM \\ 
\textbf{Est. effort:} 6h, GPU=False \\ 

\subsection*{\#5 — Enhancing training of physics-informed neural networks using domain-decomposition based preconditioning strategies}
\textbf{Score:} 18 \quad \textbf{Priority:} A \quad \textbf{Topic:} ML-operator/PINN \quad \textbf{Year:} 2023 \quad \textbf{Cites:} 28

\textit{Authors:} Alena Kopanicáková;Hardik Kothari;G. Karniadakis;Rolf Krause \\ 
\textit{DOI:} \url{https://doi.org/10.1137/23M1583375} \\ 
\textbf{Reproducibility } (10/10): full-pdf-available; code-claimed; methods:finite element,multigrid,pinn,neural network; tools:pytorch; tests:burgers,allen-cahn,advection; conv-table \\ 
\textbf{Interest } (8/10): recent; active-ml-qc; good-benchmark \\ 
\textbf{Core method:} finite element \\ 
\textbf{Test problems:} burgers, allen-cahn, advection \\ 
\textbf{Tools:} PyTorch or JAX \\ 
\textbf{Est. effort:} 6h, GPU=True \\ 

\subsection*{\#6 — Machine learning–accelerated computational fluid dynamics}
\textbf{Score:} 17 \quad \textbf{Priority:} A \quad \textbf{Topic:} ML-operator/PINN \quad \textbf{Year:} 2021 \quad \textbf{Cites:} 1123

\textit{Authors:} Dmitrii Kochkov;Jamie A. Smith;Ayya Alieva;Qing Wang;M. Brenner;Stephan Hoyer \\ 
\textit{DOI:} \url{https://doi.org/10.1073/pnas.2101784118} \\ 
\textbf{Reproducibility } (8/10): full-pdf-available; methods:finite element,finite difference,finite volume,spectral; tools:jax; tests:navier-stokes,advection,diffusion; conv-table; benchmark \\ 
\textbf{Interest } (9/10): high-cite:1123; active-ml-qc; good-benchmark \\ 
\textbf{Core method:} finite element \\ 
\textbf{Test problems:} navier-stokes, advection, diffusion \\ 
\textbf{Tools:} PyTorch, JAX \\ 
\textbf{Est. effort:} 6h, GPU=False \\ 
\textbf{Risks:} no public code \\ 

\subsection*{\#7 — Dedalus: A flexible framework for numerical simulations with spectral methods}
\textbf{Score:} 16 \quad \textbf{Priority:} B \quad \textbf{Topic:} Fluid/NavierStokes \quad \textbf{Year:} 2019 \quad \textbf{Cites:} 485

\textit{Authors:} K. Burns;G. Vasil;J. Oishi;D. Lecoanet;B. Brown \\ 
\textit{DOI:} \url{https://doi.org/10.1103/PhysRevResearch.2.023068} \\ 
\textbf{Reproducibility } (10/10): full-pdf-available; github:github.com/DedalusProject/methods\_paper\_examples; methods:finite difference,finite volume,spectral,runge-kutta; tools:fenics,firedrake,julia; tests:poisson,navier-stokes,helmholtz; benchmark \\ 
\textbf{Interest } (6/10): cited:485 \\ 
\textbf{Core method:} finite difference \\ 
\textbf{Test problems:} poisson, navier-stokes, helmholtz \\ 
\textbf{Tools:} FEniCS, OpenFOAM \\ 
\textbf{Est. effort:} 6h, GPU=False \\ 

\subsection*{\#8 — Physics-informed neural networks for solving Reynolds-averaged Navier-Stokes equations}
\textbf{Score:} 16 \quad \textbf{Priority:} A \quad \textbf{Topic:} Fluid/NavierStokes \quad \textbf{Year:} 2021 \quad \textbf{Cites:} 404

\textit{Authors:} Hamidreza Eivazi;Mojtaba Tahani;P. Schlatter;R. Vinuesa \\ 
\textit{DOI:} \url{https://doi.org/10.1063/5.0095270} \\ 
\textbf{Reproducibility } (8/10): full-pdf-available; methods:spectral,imex,pinn,neural network; tools:tensorflow; tests:navier-stokes,stokes; benchmark \\ 
\textbf{Interest } (8/10): cited:404; active-ml-qc \\ 
\textbf{Core method:} spectral \\ 
\textbf{Test problems:} navier-stokes, stokes \\ 
\textbf{Tools:} PyTorch or JAX \\ 
\textbf{Est. effort:} 8h, GPU=True \\ 
\textbf{Risks:} no public code \\ 

\subsection*{\#9 — Learning in Modal Space: Solving Time-Dependent Stochastic PDEs Using Physics-Informed Neural Networks}
\textbf{Score:} 16 \quad \textbf{Priority:} A \quad \textbf{Topic:} ML-operator/PINN \quad \textbf{Year:} 2019 \quad \textbf{Cites:} 274

\textit{Authors:} Dongkun Zhang;Ling Guo;G. Karniadakis \\ 
\textit{DOI:} \url{https://doi.org/10.1137/19m1260141} \\ 
\textbf{Reproducibility } (8/10): full-pdf-available; methods:spectral,monte carlo,pinn,neural network; tools:tensorflow; tests:burgers,navier-stokes,advection; conv-table; benchmark \\ 
\textbf{Interest } (8/10): cited:274; active-ml-qc; good-benchmark \\ 
\textbf{Core method:} spectral \\ 
\textbf{Test problems:} burgers, navier-stokes, advection \\ 
\textbf{Tools:} PyTorch or JAX \\ 
\textbf{Est. effort:} 6h, GPU=True \\ 
\textbf{Risks:} no public code \\ 

\subsection*{\#10 — Poisson Flow Generative Models}
\textbf{Score:} 16 \quad \textbf{Priority:} A \quad \textbf{Topic:} Elliptic \quad \textbf{Year:} 2022 \quad \textbf{Cites:} 115

\textit{Authors:} Yilun Xu;Ziming Liu;M. Tegmark;T. Jaakkola \\ 
\textit{DOI:} \url{https://doi.org/10.48550/arXiv.2209.11178} \\ 
\textbf{Reproducibility } (8/10): full-pdf-available; github:github.com/Newbeeer/poisson\_flow.; methods:spectral,runge-kutta,neural network; tests:poisson,diffusion \\ 
\textbf{Interest } (8/10): cited:115; recent \\ 
\textbf{Core method:} spectral \\ 
\textbf{Test problems:} poisson, diffusion \\ 
\textbf{Tools:} FEniCS, PETSc \\ 
\textbf{Est. effort:} 2h, GPU=False \\ 


\section{Full 100 Ranked Table}

\begin{center}
\scriptsize
\begin{longtable}{rrp{0.40\textwidth}cccccp{0.13\textwidth}}
\toprule
\textbf{Rk} & \textbf{Sc} & \textbf{Title} & \textbf{Pr} & \textbf{Yr} & \textbf{Ci} & \textbf{Rp} & \textbf{In} & \textbf{Topic} \\
\midrule
\endhead
1 & 19 & Can physics-informed neural networks beat the finite element method? & A & 2023 & 188 & 10 & 9 & ML-operator/PINN \\
2 & 18 & Solving High-Dimensional PDEs with Latent Spectral Models & A & 2023 & 95 & 10 & 8 & ML-operator/PINN \\
3 & 18 & Koopman neural operator as a mesh-free solver of non-linear partial differential equations & A & 2023 & 74 & 10 & 8 & ML-operator/PINN \\
4 & 18 & Lifex-cfd: an Open-source Computational Fluid Dynamics Solver for Cardiovascular Applicati… & A & 2023 & 61 & 10 & 8 & Fluid/NavierStok… \\
5 & 18 & Enhancing training of physics-informed neural networks using domain-decomposition based pr… & A & 2023 & 28 & 10 & 8 & ML-operator/PINN \\
6 & 17 & Machine learning–accelerated computational fluid dynamics & A & 2021 & 1123 & 8 & 9 & ML-operator/PINN \\
7 & 16 & Dedalus: A flexible framework for numerical simulations with spectral methods & B & 2019 & 485 & 10 & 6 & Fluid/NavierStok… \\
8 & 16 & Physics-informed neural networks for solving Reynolds-averaged Navier-Stokes equations & A & 2021 & 404 & 8 & 8 & Fluid/NavierStok… \\
9 & 16 & Learning in Modal Space: Solving Time-Dependent Stochastic PDEs Using Physics-Informed Neu… & A & 2019 & 274 & 8 & 8 & ML-operator/PINN \\
10 & 16 & Poisson Flow Generative Models & A & 2022 & 115 & 8 & 8 & Elliptic \\
11 & 16 & LNO: Laplace Neural Operator for Solving Differential Equations & A & 2023 & 56 & 8 & 8 & ML-operator/PINN \\
12 & 16 & Walk on Stars: A Grid-Free Monte Carlo Method for PDEs with Neumann Boundary Conditions & A & 2023 & 48 & 8 & 8 & Elliptic \\
13 & 16 & Fast Poisson solvers for spectral methods & B & 2017 & 47 & 10 & 6 & Elliptic \\
14 & 16 & Deep Reinforcement Learning for Adaptive Mesh Refinement & A & 2022 & 35 & 8 & 8 & AMR/Multigrid \\
15 & 16 & Godunov loss functions for modelling of hyperbolic conservation laws & A & 2024 & 5 & 8 & 8 & Hyperbolic \\
16 & 15 & Plane Wave Discontinuous Galerkin Methods for the 2D Helmholtz Equation: Analysis of the p… & B & 2011 & 199 & 7 & 8 & Helmholtz/Wave \\
17 & 15 & Galerkin Approximations for the Stochastic Burgers Equation & B & 2013 & 105 & 7 & 8 & NonlinearScalar \\
18 & 15 & FLUPS: A Fourier-Based Library of Unbounded Poisson Solvers & B & 2020 & 18 & 9 & 6 & Elliptic \\
19 & 15 & Kernel‐based active subspaces with application to computational fluid dynamics parametric … & B & 2020 & 15 & 10 & 5 & Hyperbolic \\
20 & 15 & On the convergence of discontinuous Galerkin/Hermite spectral methods for the Vlasov-Poiss… & A & 2022 & 6 & 8 & 7 & Elliptic \\
21 & 14 & Improvements to the APBS biomolecular solvation software suite & B & 2017 & 2081 & 6 & 8 & Elliptic \\
22 & 14 & Fast Nonsymmetric Iterations and Preconditioning for Navier-Stokes Equations & B & 1996 & 258 & 8 & 6 & Fluid/NavierStok… \\
23 & 14 & New Laplace and Helmholtz solvers & B & 2019 & 51 & 8 & 6 & Helmholtz/Wave \\
24 & 14 & Stability and error analysis of a class of high-order IMEX schemes for Navier-stokes equat… & B & 2021 & 43 & 8 & 6 & Fluid/NavierStok… \\
25 & 14 & Rate optimality of adaptive finite element methods with respect to the overall computation… & B & 2020 & 34 & 8 & 6 & Elliptic \\
26 & 14 & Comparison of Adaptive Multiresolution and Adaptive Mesh Refinement Applied to Simulations… & B & 2015 & 33 & 8 & 6 & AMR/Multigrid \\
27 & 14 & Kinetic.jl: A portable finite volume toolbox for scientific and neural computing & B & 2021 & 17 & 8 & 6 & ML-operator/PINN \\
28 & 14 & Highly efficient and energy dissipative schemes for the time fractional Allen-Cahn equatio… & B & 2021 & 17 & 8 & 6 & PhaseField/RD \\
29 & 14 & Modified Poisson-Nernst-Planck Model with Coulomb and Hard-sphere Correlations & B & 2020 & 15 & 8 & 6 & Elliptic \\
30 & 13 & Optimized Schwarz Methods without Overlap for the Helmholtz Equation & B & 2002 & 403 & 7 & 6 & Helmholtz/Wave \\
31 & 13 & Space-Time Continuous Analysis of Waveform Relaxation for the Heat Equation & B & 1998 & 208 & 7 & 6 & Heat/Diffusion \\
32 & 13 & Variational quantum algorithm for the Poisson equation & C & 2020 & 108 & 5 & 8 & Elliptic \\
33 & 13 & A fully discrete approximation of the one-dimensional stochastic heat equation & B & 2015 & 90 & 7 & 6 & Stochastic \\
34 & 13 & Numerical and exact solutions for time fractional Burgers' equation & B & 2017 & 66 & 7 & 6 & NonlinearScalar \\
35 & 13 & Variational quantum algorithm based on the minimum potential energy for solving the Poisso… & B & 2021 & 62 & 7 & 6 & Elliptic \\
36 & 13 & Learning Poisson Systems and Trajectories of Autonomous Systems via Poisson Neural Network… & B & 2020 & 60 & 6 & 7 & Elliptic \\
37 & 13 & A geometric multiscale model for the numerical simulation of blood flow in the human left … & B & 2021 & 48 & 8 & 5 & Fluid/NavierStok… \\
38 & 13 & Lessons for adaptive mesh refinement in numerical relativity & B & 2021 & 47 & 7 & 6 & Fluid/NavierStok… \\
39 & 13 & Analog quantum simulation of partial differential equations & B & 2023 & 47 & 6 & 7 & Quantum/Kinetic \\
40 & 13 & Gmunu: toward multigrid based Einstein field equations solver for general-relativistic hyd… & B & 2020 & 21 & 8 & 5 & Relativity/GR \\
41 & 13 & A Multivariate Spline based Collocation Method for Numerical Solution of Partial Different… & B & 2021 & 11 & 7 & 6 & Elliptic \\
42 & 13 & Retrieval of Timewise Coefficients in the Heat Equation from Nonlocal Overdetermination Co… & B & 2022 & 9 & 7 & 6 & Heat/Diffusion \\
43 & 13 & Numerical Solution to Recover Time-dependent Coefficient and Free Boundary from Nonlocal a… & B & 2021 & 8 & 7 & 6 & Heat/Diffusion \\
44 & 13 & WaveTrain: A Python package for numerical quantum mechanics of chain-like systems based on… & B & 2023 & 2 & 8 & 5 & Quantum/Kinetic \\
45 & 12 & Modelica Buildings library & C & 2014 & 769 & 4 & 8 & Fluid/NavierStok… \\
46 & 12 & Numerical methods for nonlocal and fractional models & B & 2020 & 200 & 6 & 6 & Fractional \\
47 & 12 & Action Principle for Newtonian Gravity. & B & 2018 & 144 & 6 & 6 & Fluid/NavierStok… \\
48 & 12 & Dielectric continuum methods for quantum chemistry & B & 2021 & 141 & 6 & 6 & Quantum/Kinetic \\
49 & 12 & Operator splitting for partial differential equations with Burgers nonlinearity & B & 2011 & 109 & 6 & 6 & NonlinearScalar \\
50 & 12 & A Low-Rank Projector-Splitting Integrator for the Vlasov-Poisson Equation & B & 2018 & 103 & 6 & 6 & Elliptic \\
51 & 12 & Characterization of Radially Symmetric Finite Time Blowup in Multidimensional Aggregation … & B & 2012 & 60 & 6 & 6 & Fluid/NavierStok… \\
52 & 12 & New closed form solutions of some nonlinear pseudo-parabolic models via a new extended dir… & B & 2023 & 49 & 6 & 6 & NonlinearScalar \\
53 & 12 & Error estimate of a decoupled numerical scheme for the Cahn-Hilliard-Stokes-Darcy system & B & 2021 & 41 & 6 & 6 & PhaseField/RD \\
54 & 12 & A Time-Stepping DPG Scheme for the Heat Equation & B & 2016 & 24 & 7 & 5 & Heat/Diffusion \\
55 & 12 & Depth analysis of variational quantum algorithms for the heat equation & B & 2022 & 21 & 6 & 6 & Quantum/Kinetic \\
56 & 12 & A Review on Burgers' Equations and It's Applications & B & 2023 & 8 & 6 & 6 & NonlinearScalar \\
57 & 12 & NodePy: A package for the analysis of numerical ODE solvers & C & 2020 & 8 & 8 & 4 & Other \\
58 & 12 & Numerical Solution for Two-Sided Stefan Problem & B & 2020 & 7 & 6 & 6 & FreeBoundary \\
59 & 12 & An Application of Computational Fluid Dynamics to Optimize Municipal Sewage Networks; A Ca… & C & 2020 & 4 & 8 & 4 & Fluid/NavierStok… \\
60 & 11 & The well-posedness of the Kuramoto-Sivashinsky equation & C & 1986 & 149 & 5 & 6 & NonlinearScalar \\
61 & 11 & Symmetry preserving numerical schemes for partial differential equations and their numeric… & B & 2011 & 47 & 6 & 5 & NonlinearScalar \\
62 & 11 & The Wave Breaking for Whitham-Type Equations Revisited & C & 2020 & 33 & 5 & 6 & NonlinearScalar \\
63 & 11 & Discrete Maximum principle of a high order finite difference scheme for a generalized Alle… & B & 2021 & 28 & 6 & 5 & PhaseField/RD \\
64 & 11 & Assorted exact explicit solutions for the generalized Atangana’s fractional BBM–Burgers eq… & B & 2022 & 19 & 6 & 5 & NonlinearScalar \\
65 & 11 & Nonlinear stability of planar viscous shock wave to three-dimensional compressible Navier–… & B & 2022 & 17 & 6 & 5 & Fluid/NavierStok… \\
66 & 10 & Heat and mass transfer & C & 2025 & 1552 & 2 & 8 & Fluid/NavierStok… \\
67 & 10 & Newton-GMRES Preconditioning for Discontinuous Galerkin Discretizations of the Navier--Sto… & C & 2008 & 259 & 4 & 6 & Hyperbolic \\
68 & 10 & Non-uniqueness of Leray solutions of the forced Navier-Stokes equations & C & 2021 & 153 & 4 & 6 & Fluid/NavierStok… \\
69 & 10 & Multiplicative stochastic heat equations on the whole space & C & 2015 & 138 & 4 & 6 & Stochastic \\
70 & 10 & A new technology for solving diffusion and heat equations & C & 2017 & 106 & 3 & 7 & Heat/Diffusion \\
71 & 10 & Stochastic heat equation with rough dependence in space & C & 2015 & 88 & 4 & 6 & Stochastic \\
72 & 10 & A Comparative Study of the Explicit Finite Difference Method and Physics-Informed Neural N… & C & 2023 & 29 & 4 & 6 & ML-operator/PINN \\
73 & 10 & On second-order and fourth-order elliptic systems consisting of bulk and surface PDEs: Wel… & C & 2020 & 23 & 6 & 4 & Elliptic \\
74 & 10 & ISWFoam: A numerical model for internal solitary wave simulation in continuously stratifie… & C & 2021 & 21 & 6 & 4 & Fluid/NavierStok… \\
75 & 9 & Is the Pollution Effect of the FEM Avoidable for the Helmholtz Equation Considering High W… & C & 1997 & 703 & 3 & 6 & Helmholtz/Wave \\
76 & 9 & Global Solutions of the Navier-Stokes Equations for Multidimensional Compressible Flow wit… & C & 1995 & 589 & 3 & 6 & Fluid/NavierStok… \\
77 & 9 & On splitting methods for Schrödinger-Poisson and cubic nonlinear Schrödinger equations & C & 2008 & 339 & 3 & 6 & Elliptic \\
78 & 9 & A locally conservative LDG method for the incompressible Navier-Stokes equations & C & 2004 & 329 & 4 & 5 & Fluid/NavierStok… \\
79 & 9 & Krylov methods for the incompressible Navier-Stokes equations & C & 1994 & 263 & 4 & 5 & Fluid/NavierStok… \\
80 & 9 & Feedback Boundary Stabilization of the Two-Dimensional Navier--Stokes Equations & C & 2006 & 149 & 3 & 6 & Fluid/NavierStok… \\
81 & 9 & Spectral discretization of Darcy's equations coupled with the heat equation & C & 2016 & 36 & 4 & 5 & Heat/Diffusion \\
82 & 9 & An integrated stairwise adaptive finite point scheme for the two-dimensional coupled Burge… & C & 2024 & 4 & 3 & 6 & NonlinearScalar \\
83 & 8 & Hardy Inequalities and Some Critical Elliptic and Parabolic Problems & C & 1998 & 577 & 2 & 6 & Elliptic \\
84 & 8 & Critical Exponent for a Nonlinear Wave Equation with Damping & C & 2000 & 451 & 3 & 5 & Helmholtz/Wave \\
85 & 8 & On error estimates of the projection methods for the Navier-Stokes equations: Second-order… & C & 1996 & 277 & 3 & 5 & Fluid/NavierStok… \\
86 & 8 & Conformable heat equation on a radial symmetric plate & C & 2017 & 35 & 2 & 6 & Heat/Diffusion \\
87 & 8 & Numerical Simulation of Turbulent Flow and Pollutant Dispersion in Urban Street Canyons & C & 2019 & 26 & 4 & 4 & Fluid/NavierStok… \\
88 & 8 & Fluctuations of two-dimensional stochastic heat equation and KPZ equation in subcritical r… & C & 2021 & 16 & 4 & 4 & Stochastic \\
89 & 8 & Numerical simulation of flow over buildings using OpenFOAM® & C & 2019 & 10 & 4 & 4 & Fluid/NavierStok… \\
90 & 8 & 3D Modeling and Mechanism Analysis of Breaking Wave-Induced Seabed Scour around Monopile & C & 2020 & 9 & 4 & 4 & Fluid/NavierStok… \\
91 & 8 & Numerical Simulation of Non-Darcy Flow in Naturally Fractured Tight Gas Reservoirs for Enh… & C & 2024 & 5 & 3 & 5 & Porous/Darcy \\
92 & 8 & A 2D Model for 3D Periodic Deep-Water Waves & C & 2022 & 5 & 2 & 6 & Elliptic \\
93 & 8 & Accuracy Verification of a 2D Adaptive Mesh Refinement Method Using Backward-Facing Step F… & C & 2020 & 3 & 4 & 4 & Fluid/NavierStok… \\
94 & 7 & Remarkable statistical behavior for truncated Burgers-Hopf dynamics. & C & 2000 & 115 & 2 & 5 & NonlinearScalar \\
95 & 7 & Off-fault plasticity in three-dimensional dynamic rupture simulations using a modal Discon… & C & 2018 & 86 & 2 & 5 & Hyperbolic \\
96 & 7 & Minimal controllability time for the heat equation under unilateral state or control const… & C & 2017 & 54 & 2 & 5 & Heat/Diffusion \\
97 & 7 & A Crank-Nicolson Approximation for the time Fractional Burgers Equation & C & 2020 & 29 & 3 & 4 & NonlinearScalar \\
98 & 7 & Solving one- and two-dimensional unsteady Burgers' equation using fully implicit finite di… & C & 2019 & 27 & 3 & 4 & NonlinearScalar \\
99 & 7 & Simultaneous Identification of Thermal Conductivity and Heat Source in the Heat Equation & C & 2021 & 11 & 3 & 4 & Heat/Diffusion \\
100 & 6 & Fractal Burgers Equations & C & 1998 & 222 & 1 & 5 & NonlinearScalar \\
\bottomrule
\end{longtable}
\end{center}

\section{Priority A — Ready to Go}

\textbf{\#1 [19]} — Can physics-informed neural networks beat the finite element method? \\
\textit{ML-operator/PINN, 2023, 188 cites}. Method: finite element; Tools: PyTorch or JAX; Est: 4h.

\textbf{\#2 [18]} — Solving High-Dimensional PDEs with Latent Spectral Models \\
\textit{ML-operator/PINN, 2023, 95 cites}. Method: finite element; Tools: PyTorch or JAX; Est: 4h.

\textbf{\#3 [18]} — Koopman neural operator as a mesh-free solver of non-linear partial differential equations \\
\textit{ML-operator/PINN, 2023, 74 cites}. Method: finite element; Tools: PyTorch or JAX; Est: 4h.

\textbf{\#4 [18]} — Lifex-cfd: an Open-source Computational Fluid Dynamics Solver for Cardiovascular Applications \\
\textit{Fluid/NavierStokes, 2023, 61 cites}. Method: finite element; Tools: FEniCS, OpenFOAM; Est: 6h.

\textbf{\#5 [18]} — Enhancing training of physics-informed neural networks using domain-decomposition based precondition… \\
\textit{ML-operator/PINN, 2023, 28 cites}. Method: finite element; Tools: PyTorch or JAX; Est: 6h.

\textbf{\#6 [17]} — Machine learning–accelerated computational fluid dynamics \\
\textit{ML-operator/PINN, 2021, 1123 cites}. Method: finite element; Tools: PyTorch, JAX; Est: 6h. Risks: no public code.

\textbf{\#8 [16]} — Physics-informed neural networks for solving Reynolds-averaged Navier-Stokes equations \\
\textit{Fluid/NavierStokes, 2021, 404 cites}. Method: spectral; Tools: PyTorch or JAX; Est: 8h. Risks: no public code.

\textbf{\#9 [16]} — Learning in Modal Space: Solving Time-Dependent Stochastic PDEs Using Physics-Informed Neural Networ… \\
\textit{ML-operator/PINN, 2019, 274 cites}. Method: spectral; Tools: PyTorch or JAX; Est: 6h. Risks: no public code.

\textbf{\#10 [16]} — Poisson Flow Generative Models \\
\textit{Elliptic, 2022, 115 cites}. Method: spectral; Tools: FEniCS, PETSc; Est: 2h.

\textbf{\#11 [16]} — LNO: Laplace Neural Operator for Solving Differential Equations \\
\textit{ML-operator/PINN, 2023, 56 cites}. Method: neural network; Tools: PyTorch or JAX; Est: 6h. Risks: no public code.

\textbf{\#12 [16]} — Walk on Stars: A Grid-Free Monte Carlo Method for PDEs with Neumann Boundary Conditions \\
\textit{Elliptic, 2023, 48 cites}. Method: finite element; Tools: FEniCS, PETSc; Est: 3h. Risks: no public code.

\textbf{\#14 [16]} — Deep Reinforcement Learning for Adaptive Mesh Refinement \\
\textit{AMR/Multigrid, 2022, 35 cites}. Method: finite element; Tools: deal.II, AMReX; Est: 8h. Risks: no public code.

\textbf{\#15 [16]} — Godunov loss functions for modelling of hyperbolic conservation laws \\
\textit{Hyperbolic, 2024, 5 cites}. Method: finite difference; Tools: PyTorch or JAX; Est: 5h. Risks: no public code.

\textbf{\#20 [15]} — On the convergence of discontinuous Galerkin/Hermite spectral methods for the Vlasov-Poisson system \\
\textit{Elliptic, 2022, 6 cites}. Method: finite element; Tools: FEniCS, PETSc; Est: 3h. Risks: no public code.


\section{Priority B — Needs Minor Work}

\#7 [16] Dedalus: A flexible framework for numerical simulations with spectral methods — Fluid/NavierStokes, 6h.

\#13 [16] Fast Poisson solvers for spectral methods — Elliptic, 2h.

\#16 [15] Plane Wave Discontinuous Galerkin Methods for the 2D Helmholtz Equation: Analysis of the p… — Helmholtz/Wave, 4h.

\#17 [15] Galerkin Approximations for the Stochastic Burgers Equation — NonlinearScalar, 3h.

\#18 [15] FLUPS: A Fourier-Based Library of Unbounded Poisson Solvers — Elliptic, 2h.

\#19 [15] Kernel‐based active subspaces with application to computational fluid dynamics parametric … — Hyperbolic, 3h.

\#21 [14] Improvements to the APBS biomolecular solvation software suite — Elliptic, 3h.

\#22 [14] Fast Nonsymmetric Iterations and Preconditioning for Navier-Stokes Equations — Fluid/NavierStokes, 8h.

\#23 [14] New Laplace and Helmholtz solvers — Helmholtz/Wave, 4h.

\#24 [14] Stability and error analysis of a class of high-order IMEX schemes for Navier-stokes equat… — Fluid/NavierStokes, 8h.

\#25 [14] Rate optimality of adaptive finite element methods with respect to the overall computation… — Elliptic, 3h.

\#26 [14] Comparison of Adaptive Multiresolution and Adaptive Mesh Refinement Applied to Simulations… — AMR/Multigrid, 6h.

\#27 [14] Kinetic.jl: A portable finite volume toolbox for scientific and neural computing — ML-operator/PINN, 6h.

\#28 [14] Highly efficient and energy dissipative schemes for the time fractional Allen-Cahn equatio… — PhaseField/RD, 5h.

\#29 [14] Modified Poisson-Nernst-Planck Model with Coulomb and Hard-sphere Correlations — Elliptic, 3h.

\#30 [13] Optimized Schwarz Methods without Overlap for the Helmholtz Equation — Helmholtz/Wave, 4h.

\#31 [13] Space-Time Continuous Analysis of Waveform Relaxation for the Heat Equation — Heat/Diffusion, 3h.

\#33 [13] A fully discrete approximation of the one-dimensional stochastic heat equation — Stochastic, 4h.

\#34 [13] Numerical and exact solutions for time fractional Burgers' equation — NonlinearScalar, 3h.

\#35 [13] Variational quantum algorithm based on the minimum potential energy for solving the Poisso… — Elliptic, 2h.

\#36 [13] Learning Poisson Systems and Trajectories of Autonomous Systems via Poisson Neural Network… — Elliptic, 3h.

\#37 [13] A geometric multiscale model for the numerical simulation of blood flow in the human left … — Fluid/NavierStokes, 8h.

\#38 [13] Lessons for adaptive mesh refinement in numerical relativity — Fluid/NavierStokes, 8h.

\#39 [13] Analog quantum simulation of partial differential equations — Quantum/Kinetic, 6h.

\#40 [13] Gmunu: toward multigrid based Einstein field equations solver for general-relativistic hyd… — Relativity/GR, 12h.

\#41 [13] A Multivariate Spline based Collocation Method for Numerical Solution of Partial Different… — Elliptic, 3h.

\#42 [13] Retrieval of Timewise Coefficients in the Heat Equation from Nonlocal Overdetermination Co… — Heat/Diffusion, 3h.

\#43 [13] Numerical Solution to Recover Time-dependent Coefficient and Free Boundary from Nonlocal a… — Heat/Diffusion, 3h.

\#44 [13] WaveTrain: A Python package for numerical quantum mechanics of chain-like systems based on… — Quantum/Kinetic, 4h.

\#46 [12] Numerical methods for nonlocal and fractional models — Fractional, 4h.

\#47 [12] Action Principle for Newtonian Gravity. — Fluid/NavierStokes, 8h.

\#48 [12] Dielectric continuum methods for quantum chemistry — Quantum/Kinetic, 6h.

\#49 [12] Operator splitting for partial differential equations with Burgers nonlinearity — NonlinearScalar, 3h.

\#50 [12] A Low-Rank Projector-Splitting Integrator for the Vlasov-Poisson Equation — Elliptic, 3h.

\#51 [12] Characterization of Radially Symmetric Finite Time Blowup in Multidimensional Aggregation … — Fluid/NavierStokes, 8h.

\#52 [12] New closed form solutions of some nonlinear pseudo-parabolic models via a new extended dir… — NonlinearScalar, 3h.

\#53 [12] Error estimate of a decoupled numerical scheme for the Cahn-Hilliard-Stokes-Darcy system — PhaseField/RD, 5h.

\#54 [12] A Time-Stepping DPG Scheme for the Heat Equation — Heat/Diffusion, 3h.

\#55 [12] Depth analysis of variational quantum algorithms for the heat equation — Quantum/Kinetic, 6h.

\#56 [12] A Review on Burgers' Equations and It's Applications — NonlinearScalar, 3h.

\#58 [12] Numerical Solution for Two-Sided Stefan Problem — FreeBoundary, 5h.

\#61 [11] Symmetry preserving numerical schemes for partial differential equations and their numeric… — NonlinearScalar, 3h.

\#63 [11] Discrete Maximum principle of a high order finite difference scheme for a generalized Alle… — PhaseField/RD, 5h.

\#64 [11] Assorted exact explicit solutions for the generalized Atangana’s fractional BBM–Burgers eq… — NonlinearScalar, 3h.

\#65 [11] Nonlinear stability of planar viscous shock wave to three-dimensional compressible Navier–… — Fluid/NavierStokes, 8h.


\section{Priority C — Hard (defer or skip)}

\#32 [13] Variational quantum algorithm for the Poisson equation — Elliptic.

\#45 [12] Modelica Buildings library — Fluid/NavierStokes.

\#57 [12] NodePy: A package for the analysis of numerical ODE solvers — Other.

\#59 [12] An Application of Computational Fluid Dynamics to Optimize Municipal Sewage Networks; A Ca… — Fluid/NavierStokes.

\#60 [11] The well-posedness of the Kuramoto-Sivashinsky equation — NonlinearScalar.

\#62 [11] The Wave Breaking for Whitham-Type Equations Revisited — NonlinearScalar.

\#66 [10] Heat and mass transfer — Fluid/NavierStokes.

\#67 [10] Newton-GMRES Preconditioning for Discontinuous Galerkin Discretizations of the Navier--Sto… — Hyperbolic.

\#68 [10] Non-uniqueness of Leray solutions of the forced Navier-Stokes equations — Fluid/NavierStokes.

\#69 [10] Multiplicative stochastic heat equations on the whole space — Stochastic.

\#70 [10] A new technology for solving diffusion and heat equations — Heat/Diffusion.

\#71 [10] Stochastic heat equation with rough dependence in space — Stochastic.

\#72 [10] A Comparative Study of the Explicit Finite Difference Method and Physics-Informed Neural N… — ML-operator/PINN.

\#73 [10] On second-order and fourth-order elliptic systems consisting of bulk and surface PDEs: Wel… — Elliptic.

\#74 [10] ISWFoam: A numerical model for internal solitary wave simulation in continuously stratifie… — Fluid/NavierStokes.

\#75 [9] Is the Pollution Effect of the FEM Avoidable for the Helmholtz Equation Considering High W… — Helmholtz/Wave.

\#76 [9] Global Solutions of the Navier-Stokes Equations for Multidimensional Compressible Flow wit… — Fluid/NavierStokes.

\#77 [9] On splitting methods for Schrödinger-Poisson and cubic nonlinear Schrödinger equations — Elliptic.

\#78 [9] A locally conservative LDG method for the incompressible Navier-Stokes equations — Fluid/NavierStokes.

\#79 [9] Krylov methods for the incompressible Navier-Stokes equations — Fluid/NavierStokes.

\#80 [9] Feedback Boundary Stabilization of the Two-Dimensional Navier--Stokes Equations — Fluid/NavierStokes.

\#81 [9] Spectral discretization of Darcy's equations coupled with the heat equation — Heat/Diffusion.

\#82 [9] An integrated stairwise adaptive finite point scheme for the two-dimensional coupled Burge… — NonlinearScalar.

\#83 [8] Hardy Inequalities and Some Critical Elliptic and Parabolic Problems — Elliptic.

\#84 [8] Critical Exponent for a Nonlinear Wave Equation with Damping — Helmholtz/Wave.

\#85 [8] On error estimates of the projection methods for the Navier-Stokes equations: Second-order… — Fluid/NavierStokes.

\#86 [8] Conformable heat equation on a radial symmetric plate — Heat/Diffusion.

\#87 [8] Numerical Simulation of Turbulent Flow and Pollutant Dispersion in Urban Street Canyons — Fluid/NavierStokes.

\#88 [8] Fluctuations of two-dimensional stochastic heat equation and KPZ equation in subcritical r… — Stochastic.

\#89 [8] Numerical simulation of flow over buildings using OpenFOAM® — Fluid/NavierStokes.

\#90 [8] 3D Modeling and Mechanism Analysis of Breaking Wave-Induced Seabed Scour around Monopile — Fluid/NavierStokes.

\#91 [8] Numerical Simulation of Non-Darcy Flow in Naturally Fractured Tight Gas Reservoirs for Enh… — Porous/Darcy.

\#92 [8] A 2D Model for 3D Periodic Deep-Water Waves — Elliptic.

\#93 [8] Accuracy Verification of a 2D Adaptive Mesh Refinement Method Using Backward-Facing Step F… — Fluid/NavierStokes.

\#94 [7] Remarkable statistical behavior for truncated Burgers-Hopf dynamics. — NonlinearScalar.

\#95 [7] Off-fault plasticity in three-dimensional dynamic rupture simulations using a modal Discon… — Hyperbolic.

\#96 [7] Minimal controllability time for the heat equation under unilateral state or control const… — Heat/Diffusion.

\#97 [7] A Crank-Nicolson Approximation for the time Fractional Burgers Equation — NonlinearScalar.

\#98 [7] Solving one- and two-dimensional unsteady Burgers' equation using fully implicit finite di… — NonlinearScalar.

\#99 [7] Simultaneous Identification of Thermal Conductivity and Heat Source in the Heat Equation — Heat/Diffusion.

\#100 [6] Fractal Burgers Equations — NonlinearScalar.


\section{Appendix: Per-paper Reproduction Details (Top 30)}

For each of the top-30 ranked papers we list the core method, test problems, tool stack,
GPU requirement, and estimated effort.

\paragraph{\#1 — Can physics-informed neural networks beat the finite element method?}

Method: finite element. Tests: heat equation, poisson, navier-stokes. Tools: PyTorch or JAX. Est.: 4h; GPU=True. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#2 — Solving High-Dimensional PDEs with Latent Spectral Models}

Method: finite element. Tests: navier-stokes, darcy, diffusion. Tools: PyTorch or JAX. Est.: 4h; GPU=True. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#3 — Koopman neural operator as a mesh-free solver of non-linear partial differential equations}

Method: finite element. Tests: burgers, navier-stokes, stokes. Tools: PyTorch or JAX. Est.: 4h; GPU=True. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#4 — Lifex-cfd: an Open-source Computational Fluid Dynamics Solver for Cardiovascular Applications}

Method: finite element. Tests: poisson, navier-stokes, advection. Tools: FEniCS, OpenFOAM. Est.: 6h; GPU=False. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#5 — Enhancing training of physics-informed neural networks using domain-decomposition based preconditioning strate…}

Method: finite element. Tests: burgers, allen-cahn, advection. Tools: PyTorch or JAX. Est.: 6h; GPU=True. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#6 — Machine learning–accelerated computational fluid dynamics}

Method: finite element. Tests: navier-stokes, advection, diffusion. Tools: PyTorch, JAX. Est.: 6h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#7 — Dedalus: A flexible framework for numerical simulations with spectral methods}

Method: finite difference. Tests: poisson, navier-stokes, helmholtz. Tools: FEniCS, OpenFOAM. Est.: 6h; GPU=False. Expected fidelity: quantitative match on key figures. 

\paragraph{\#8 — Physics-informed neural networks for solving Reynolds-averaged Navier-Stokes equations}

Method: spectral. Tests: navier-stokes, stokes. Tools: PyTorch or JAX. Est.: 8h; GPU=True. Expected fidelity: quantitative match on key figures. Risks: no public code.

\paragraph{\#9 — Learning in Modal Space: Solving Time-Dependent Stochastic PDEs Using Physics-Informed Neural Networks}

Method: spectral. Tests: burgers, navier-stokes, advection. Tools: PyTorch or JAX. Est.: 6h; GPU=True. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#10 — Poisson Flow Generative Models}

Method: spectral. Tests: poisson, diffusion. Tools: FEniCS, PETSc. Est.: 2h; GPU=False. Expected fidelity: quantitative match on key figures. 

\paragraph{\#11 — LNO: Laplace Neural Operator for Solving Differential Equations}

Method: neural network. Tests: heat equation, diffusion, reaction-diffusion. Tools: PyTorch or JAX. Est.: 6h; GPU=True. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#12 — Walk on Stars: A Grid-Free Monte Carlo Method for PDEs with Neumann Boundary Conditions}

Method: finite element. Tests: poisson, navier-stokes, helmholtz. Tools: FEniCS, PETSc. Est.: 3h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#13 — Fast Poisson solvers for spectral methods}

Method: finite element. Tests: poisson, stokes. Tools: FEniCS, PETSc. Est.: 2h; GPU=False. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#14 — Deep Reinforcement Learning for Adaptive Mesh Refinement}

Method: finite element. Tests: poisson, schrödinger, wave equation. Tools: deal.II, AMReX. Est.: 8h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#15 — Godunov loss functions for modelling of hyperbolic conservation laws}

Method: finite difference. Tests: burgers, navier-stokes, diffusion. Tools: PyTorch or JAX. Est.: 5h; GPU=True. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#16 — Plane Wave Discontinuous Galerkin Methods for the 2D Helmholtz Equation: Analysis of the p-Version}

Method: finite element. Tests: helmholtz. Tools: FEniCS, Firedrake. Est.: 4h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#17 — Galerkin Approximations for the Stochastic Burgers Equation}

Method: finite element. Tests: burgers, heat equation, navier-stokes. Tools: SciPy, NumPy. Est.: 3h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#18 — FLUPS: A Fourier-Based Library of Unbounded Poisson Solvers}

Method: spectral. Tests: poisson, helmholtz. Tools: FEniCS, PETSc. Est.: 2h; GPU=False. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#19 — Kernel‐based active subspaces with application to computational fluid dynamics parametric problems using the d…}

Method: finite element. Tests: poisson, navier-stokes, advection. Tools: Clawpack, FEniCS. Est.: 3h; GPU=False. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#20 — On the convergence of discontinuous Galerkin/Hermite spectral methods for the Vlasov-Poisson system}

Method: finite element. Tests: poisson, diffusion, vlasov. Tools: FEniCS, PETSc. Est.: 3h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#21 — Improvements to the APBS biomolecular solvation software suite}

Method: finite element. Tests: poisson, diffusion. Tools: FEniCS, PETSc. Est.: 3h; GPU=False. Expected fidelity: quantitative match on key figures. Risks: no public code.

\paragraph{\#22 — Fast Nonsymmetric Iterations and Preconditioning for Navier-Stokes Equations}

Method: finite element. Tests: navier-stokes, diffusion, stokes. Tools: FEniCS, OpenFOAM. Est.: 8h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#23 — New Laplace and Helmholtz solvers}

Method: finite element. Tests: helmholtz. Tools: FEniCS, Firedrake. Est.: 4h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#24 — Stability and error analysis of a class of high-order IMEX schemes for Navier-stokes equations with periodic b…}

Method: finite element. Tests: poisson, navier-stokes, stokes. Tools: FEniCS, OpenFOAM. Est.: 8h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#25 — Rate optimality of adaptive finite element methods with respect to the overall computational costs}

Method: finite element. Tests: poisson, diffusion. Tools: FEniCS, PETSc. Est.: 3h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#26 — Comparison of Adaptive Multiresolution and Adaptive Mesh Refinement Applied to Simulations of the Compressible…}

Method: finite difference. Tests: specific test problem from paper. Tools: deal.II, AMReX. Est.: 6h; GPU=False. Expected fidelity: quantitative match on reported error tables. 

\paragraph{\#27 — Kinetic.jl: A portable finite volume toolbox for scientific and neural computing}

Method: finite volume. Tests: burgers, navier-stokes, advection. Tools: PyTorch or JAX, Julia. Est.: 6h; GPU=True. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#28 — Highly efficient and energy dissipative schemes for the time fractional Allen-Cahn equation}

Method: finite difference. Tests: poisson, allen-cahn, cahn-hilliard. Tools: FEniCS, PETSc. Est.: 5h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#29 — Modified Poisson-Nernst-Planck Model with Coulomb and Hard-sphere Correlations}

Method: finite difference. Tests: poisson, helmholtz, diffusion. Tools: FEniCS, PETSc. Est.: 3h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.

\paragraph{\#30 — Optimized Schwarz Methods without Overlap for the Helmholtz Equation}

Method: krylov. Tests: helmholtz, wave equation. Tools: FEniCS, Firedrake. Est.: 4h; GPU=False. Expected fidelity: quantitative match on reported error tables. Risks: no public code.


\end{document}
