\section{Deferred / Blocked Papers}\label{sec:deferred}

The following papers have well-defined upgrade paths but are currently
parked due to access or compute blockers:

\begin{itemize}[leftmargin=1.4em,itemsep=0.3em]
\item \textbf{2469515 --- PATRIC Genome Binning} (C=4, A=10).
  Blocker: SEEDtk supervised pipeline requires internal BV-BRC access.
  Access requested from M.~Shukla on 2026-04-24; pending.

\item \textbf{1275503 --- CROC Cosmic Reionization} (C=5, A=5).
  Blocker: CROC hydro code requires a Polaris allocation with $\sim$$5 \times 10^4$
  node-hours. Request in preparation.

\item \textbf{3003857 --- MP-NODE Chaotic Dynamics} (C=5, A=4).
  Blocker: full Kolmogorov cascade + ERA5 data require dedicated
  8$\times$A100 for two weeks. Partial replication complete.

\item \textbf{1559043 --- Ignition Kernel Turbulent Crossflow} (C=6, A=6).
  Blocker: Polaris 20-job ensemble needed for complete Fig.~3 replication.
  Allocation request in flight.

\item \textbf{PVMol-Gen --- Passivation Molecules Perovskite} (C=7, A=5).
  Blocker: xTB/DFT surrogate calculators needed to verify electronic-property
  filters; RDKit approximations are insufficient.

\item \textbf{34325466 --- Centenarian Bile Acid (Sato 2021)} (C=4, A=6).
  Blocker: full-depth metagenome assembly pipeline required (current
  spot-check used 3--7\% of total read depth). SRA download of full
  dataset ($\sim$1.5\,TB) is the gating step.

\item \textbf{26392213 --- Outer Mucus Niche (Li 2015)} (C=6, A=6).
  Blocker: weighted UniFrac requires phylogenetic tree construction with
  Greengenes taxonomy. Bray-Curtis proxy produced qualitatively similar but
  quantitatively weaker results.
\end{itemize}
