\section{Wave Summaries}\label{sec:waves}

\subsection{Wave 1 (2026-04 early): Foundation Cohort}
The initial wave of 30 papers was completed over approximately three weeks
using serial agent execution (one paper at a time). The cohort drew from
OSTI.gov, selecting Argonne-authored computational papers across 15+ domains.
Model backbone: GPT-4-family models, later switching to Claude Opus.
Mean coverage: 6.40/10; mean agreement: 7.17/10.
22/30 scored REPLICATED or near-REPLICATED ($\geq$7/7); 4/30 scored $\leq$5
on at least one axis. The strongest results came from pure mathematics
(integer sequences, 10/10) and graph algorithms (GraphBLAS, 9/10).

%% Full-build paper inputs for Wave 1 (papers 1--30)
\iffull
\clearpage
\section*{Wave 1: Per-Paper Evaluations}
\addcontentsline{toc}{section}{Wave 1: Per-Paper Evaluations}
\input{papers/1997354}
\input{papers/1379592}
\input{papers/1523841}
\input{papers/2441075}
\input{papers/1624105}
\input{papers/1606674}
\input{papers/1565592}
\input{papers/1461824}
\input{papers/1842593}
\input{papers/1412756}
\input{papers/2217719}
\input{papers/2439897}
\input{papers/1475143}
\input{papers/3014512}
\input{papers/2587225}
\input{papers/2571909}
\input{papers/2475938}
\input{papers/1427646}
\input{papers/1983793}
\input{papers/1484740}
\input{papers/1559043}
\input{papers/PVMol-Gen}
\input{papers/2571540}
\input{papers/1864334}
\input{papers/1981773}
\input{papers/2396968}
\input{papers/1275503}
\input{papers/1868518}
\input{papers/3003857}
\input{papers/2469515}
\fi

\subsection{Wave 2 (2026-04-26 to 2026-04-30): Scaling Out via Parallel Subagents}
Wave~2 added 15 papers in five days by running multiple replication subagents
in parallel. Key advances: subagent parallelism (3--5 concurrent sessions),
switch to Claude Opus~4 as default model, and \texttt{pack\_jobs.py} for HPC
batch throughput. Domain expansion into gravitational waves (NANOGrav),
exoplanet transits (BLS), domain LMs (NukeLM), climate emulation (fldgen),
HPC scheduling RL (DRAS), and cosmological neural emulators (CosmoPower).
The honest-negative Godunov-loss result demonstrated the pipeline's capacity
for non-confirmatory findings.

\noindent Throughput comparison:
\begin{center}
\begin{tabular}{lcc}\toprule
 & Wave~1 & Wave~2 \\\midrule
Papers completed & 30 & 15 \\
Calendar days & $\sim$21 & 5 \\
Papers/day & 1.4 & 2.8 \\
Mean coverage & 6.40 & 7.67 \\
Mean agreement & 7.17 & 8.27 \\
Agent model & GPT-4/Claude & Claude Opus~4 \\
Parallelism & Serial & 3--5 subagents \\\bottomrule
\end{tabular}
\end{center}

The 2$\times$ throughput gain is attributable to subagent parallelism,
replication-plan caching from Wave~1, and better paper selection (public
data + open code).

%% Full-build paper inputs for Wave 2 (papers 31--45)
\iffull
\clearpage
\section*{Wave 2: Per-Paper Evaluations}
\addcontentsline{toc}{section}{Wave 2: Per-Paper Evaluations}
\input{papers/1609039}
\input{papers/lightning-laplace}
\input{papers/fast-poisson-spectral}
\input{papers/2582579}
\input{papers/2587579}
\input{papers/2587945}
\input{papers/1861801}
\input{papers/1578031}
\input{papers/1993311}
\input{papers/1984484}
\input{papers/nanograv}
\input{papers/bls-exoplanet}
\input{papers/cosmopower}
\input{papers/poisson-flow}
\input{papers/godunov-loss}
\fi

\subsection{Wave 3 (2026-05-05): Biology and BV-BRC Batch}
Wave~3 added 10 biology/bioinformatics replications in a single day,
leveraging the BV-BRC API, NCBI BLAST, KEGG REST API, and local
bioinformatics tools (BLASTP, EMBOSS needle, bowtie2, SPAdes, Prokka,
Roary, FastANI, abricate). This was the first systematic batch of
microbial-genomics replications. Key advances: BV-BRC API as primary
data source (5 papers), sequence-level bioinformatics achieving the
highest precision in the cohort (Jiang~2017 matched 56/56 ARG protein
identities with mean deviation 0.3\%), and the largest-scale single-paper
replication (Price~2018: 32 organisms, 150,851 genes, 4,870 experiments).

\noindent\textbf{Wave~3 summary statistics (10 papers):}
mean coverage = 7.6/10, mean agreement = 8.1/10.
7/10 scored REPLICATED, 3/10 PARTIAL or SPOT-CHECK.
0/10 contradicted.

%% Full-build paper inputs for Wave 3 (papers 46--55)
\iffull
\clearpage
\section*{Wave 3: Per-Paper Evaluations (Biology / BV-BRC)}
\addcontentsline{toc}{section}{Wave 3: Per-Paper Evaluations (Biology / BV-BRC)}
\input{papers/28589945}
\input{papers/29769716}
\input{papers/36123438}
\input{papers/26392213}
\input{papers/34325466}
\input{papers/BVBRC-01}
\input{papers/BVBRC-02}
\input{papers/BVBRC-03}
\input{papers/BVBRC-04}
\input{papers/BVBRC-05}
\fi

\subsection{Wave 4 (2026-05-07): PDE and PINN Batch}
Wave~4 added 5 PDE/PINN replications in a single day, probing the
reproducibility of machine-learning approaches to partial differential
equations. The decisive finding: \textbf{code availability is the single
strongest predictor of replication success.} The two papers with public
GitHub repositories (Kochkov~2021 jax-cfd, Grossmann~2023 FEM-vs-PINNs)
both achieved REPLICATED status (C=8, A=9 each). The three papers without
public code (Eivazi~2022, Kopani\v{c}akov\'a~2023, Zhang~2019) all
achieved PARTIAL, with absolute errors 10--100$\times$ higher than claimed.
Wave~4 also demonstrated two creative data-blocker workarounds:
self-generating ground truth via analytical solutions (3D Poisson) and
split-step Fourier methods (1D Schr\"odinger).

\noindent\textbf{Wave~4 summary statistics (5 papers):}
mean coverage = 7.2/10, mean agreement = 7.0/10.
2/5 scored REPLICATED, 3/5 PARTIAL.
0/5 contradicted.

\subsection{Wave 5 (2026-05-10): BV-BRC Clinical Genomics Batch}
Wave~5 added 6 more BV-BRC-track replications, completing the BVBRC-01
through BVBRC-11 series. Domains span carbapenem-resistant
\textit{Klebsiella} plasmid epidemiology, ISO-compliant AMR surveillance
workflows, dairy and gut probiotic genomes, and Latin American VRE
phylogeography. The defining advance of this wave was a
\textbf{sub-2-hour, sequence-resolved phylogeny pipeline} on chiatta00
(Intel Max GPU node) that established Yuan~2019 (\textit{bla}NDM-5
plasmid epi) as the highest-precision plasmid-borne ARG replication in
the corpus (Mash distance $5.57\times10^{-4}$ to the reference plasmid).
Three papers (Kandasamy, Milerien\.{e}, R\'{i}os) achieved PARTIAL
status, all gated either by web-only annotation tools (PHASTER, BAGEL4,
KEGG BlastKOALA, antiSMASH, dbCAN, IslandViewer) or by
compute-infeasible Bayesian dating analyses (BEAST MCMC on 340-genome
global panels). Zero contradictions.

\noindent\textbf{Wave~5 summary statistics (6 papers):}
mean coverage = 8.8/10, mean agreement = 8.8/10.
3/6 scored REPLICATED, 3/6 PARTIAL.
0/6 contradicted.

%% Full-build paper inputs for Wave 5 (papers 62--67)
\iffull
\clearpage
\section*{Wave 5: Per-Paper Evaluations (BV-BRC, May 10)}
\addcontentsline{toc}{section}{Wave 5: Per-Paper Evaluations (BV-BRC, May 10)}
\input{papers/BVBRC-06}
\input{papers/BVBRC-07}
\input{papers/BVBRC-08}
\input{papers/BVBRC-09}
\input{papers/BVBRC-10}
\input{papers/BVBRC-11}
\fi

%% Full-build paper inputs for Wave 4 (papers 56--60 + PINN cross-cutting)
\iffull
\clearpage
\section*{Wave 4: Per-Paper Evaluations (PDE / PINN)}
\addcontentsline{toc}{section}{Wave 4: Per-Paper Evaluations (PDE / PINN)}
\input{papers/jax-cfd}
\input{papers/fem-vs-pinns}
\input{papers/pinn-rans}
\input{papers/pinn-domain-decomp}
\input{papers/modal-space-zhang}
\input{papers/pinn-repro-crosscutting}
\fi
