\subsection{2. Mathematical Foundations of the GraphBLAS}
\textbf{OSTI:} \texttt{1379592}\quad\textbf{Authors:} Kepner et al. (2016)\quad\textbf{Domain:} Computer Science / Graph Algorithms\\
\scorebadge{Coverage}{9}\quad\scorebadge{Agreement}{10}\quad\textbf{Total:} 19/20\par\smallskip
\noindent\textbf{Coverage rationale.} Complete from-scratch implementation of GraphBLAS algebraic foundations: Monoid, Semiring, SparseMatrix, SparseVector, plus 11 core operations (mxm, mxv, vxm, eWiseAdd, eWiseMult, extract, assign, apply, reduce, transpose, kronecker) generic over any user semiring with masking and accumulation. All 7 worked figure examples reproduced exactly. 6 classical graph algorithms (BFS, SSSP, triangles, betweenness, PageRank, CC) expressed purely via primitives. Only gap: no large-scale performance benchmarks vs SuiteSparse:GraphBLAS C reference.\par
\noindent\textbf{Agreement rationale.} Every worked figure matches exactly (12-edge adjacency, incidence products, BFS hop frontiers, etc.). All 4 quantitative algorithms (BFS, SSSP, triangles, PageRank) cross-validated against NetworkX on the paper's 7-vertex graph and extra test graphs --- all agree. 67/67 tests pass in \textless{}1s. Since the paper is definitional, 'agreement' = internal consistency + algorithm correctness, both perfect.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Monoid/Semiring algebra with 7 built-in semirings (arithmetic, tropical, boolean, max-plus, min-times, max-min, plus-min)
\item SparseMatrix/SparseVector with structural-zero semantics
\item 11 core operations generic over any semiring
\item Masking (structural, complement) and accumulation
\item All 7 paper figure examples (Figs 1,2,4,5,6,7,8)
\item 6 graph algorithms: BFS, SSSP, triangle count, betweenness, PageRank, connected components
\item Cross-validation vs NetworkX on BFS, SSSP, triangles, PageRank
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Large-scale performance benchmarks (paper is mostly definitional, so minor)
\item Comparison vs SuiteSparse:GraphBLAS C reference implementation
\item GPU-accelerated semiring operations
\item Distributed / parallel semantics (HPC scaling)
\item Streaming / incremental update operations
\item Higher-order algorithms (max-flow, graph matching) beyond the core 6
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Benchmark our Python GraphBLAS vs SuiteSparse:GraphBLAS on SNAP graphs (LiveJournal, Orkut, Friendster) for BFS, SSSP, triangle count --- what is the Python slowdown factor, and which primitives dominate
\item Express three recent graph algorithms (GNN message-passing, graph spectral clustering, personalized PageRank with teleport) as GraphBLAS primitives --- is the semiring abstraction sufficient, or what extensions are needed
\item Design a semiring for uncertainty propagation (value + variance pairs) and express variance-aware BFS and SSSP --- does the algebraic structure (associativity, distributivity) still hold, and does this yield provably-correct uncertainty quantification
\item Compare GraphBLAS-expressed triangle counting against vertex-centric (Pregel) and matrix-free (SuiteSparse LAGraph) implementations on a 10-edge graph --- at what scale does the matrix formulation beat vertex-centric, and where does each paradigm break
\item Formally verify (e.g., in Coq or Lean) that our 6 graph algorithms are correct for any abstract semiring satisfying the stated axioms --- this would provide the first machine-checked proof of GraphBLAS algorithm correctness.
\end{enumerate}

