\subsection{8. Approximating Photo-z PDFs for Large Surveys}
\textbf{OSTI:} \texttt{1461824}\quad\textbf{Authors:} Malz \& Marshall (2018)\quad\textbf{Domain:} Astrophysics / Statistical Compression\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} All three formats (histogram, samples, quantiles) implemented with paper-matching reconstruction (piecewise-constant, Gaussian KDE, PCHIP spline-CDF). Protocol matched exactly: N\_f $\in$ \{3,10,30,100\}, 10 random subsamples of 100 galaxies each, KLD + moment errors (m=1,2,3). Bright and faint synthetic catalogs (100K galaxies each) with 3/5-component GMMs. Main gap: mock catalogs are synthetic GMMs, not BPZ-processed Buzzard/Millennium simulations (not publicly available).\par
\noindent\textbf{Agreement rationale.} All qualitative claims confirmed: (1) quantiles best for broad/multimodal PDFs (KLD=0.001 vs 0.052 for histogram at N\_f=100, faint); (2) histograms best for narrow/unimodal (bright); (3) samples least efficient. Moment errors track KLD. Monotonic improvement with N\_f. Absolute KLD values same order of magnitude as paper; exact numerical comparison limited by synthetic vs. BPZ catalog differences.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Three format implementations with matching reconstruction methods
\item N\_f grid \{3, 10, 30, 100\}
\item 10 random subsamples $\times$ 100 galaxies protocol
\item KL divergence on fine grid with floor $\epsilon$=10$^3$
\item Moment errors $\Delta$, $\Delta$, $\Delta$ (mean, variance, skewness)
\item Stacked n(z) comparisons at all N\_f
\item Qualitative ordering: quantiles  histograms \textless{} samples on faint; histograms \textless{} quantiles \textless{} samples on bright
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Actual BPZ-processed mock catalogs (Graham et al. 2018 / Buzzard / Millennium)
\item Realistic photometric-noise distribution of PDF shapes
\item Paper's custom quantile-spline with linear tail extrapolation (we used PCHIP)
\item Specified KDE bandwidth (we used scipy Scott's rule)
\item Full qp-package integration
\item Storage-vs-accuracy Pareto frontier in bytes (not just N\_f)
\item Downstream cosmology-inference impact test
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Generate BPZ-like mocks from a real photometric catalog (e.g., COSMOS2020 or HSC-SSP) and re-run the KLD benchmark --- does the quantile dominance hold when the PDF shape distribution comes from real data
\item At fixed byte budget (not N\_f), which format wins Compute exact byte cost including metaparameters and float precision (float16 vs float32) --- does quantiles' advantage shrink when samples use int16 indices
\item Train a neural PDF compressor (VAE or normalizing flow) on the same mock catalogs --- does a learned 10-dim latent beat the best classical format at matched byte budget
\item How does quantile reconstruction degrade under realistic tail truncation (z quantile levels clipped to [0.01, 0.99]) Sweep clipping thresholds and identify the regime where samples format surpasses quantiles.
\item Propagate each compressed format through a 2-point cosmic-shear cosmological inference --- does the quantile format's lower KLD translate to tighter $\Omega$\_m, $\sigma$ contours, and by how many percent
\end{enumerate}

