\subsection{20. Electronic and Optical Properties of Two-Dimensional GaN from First-Principles}
\textbf{OSTI:} \texttt{1484740}\quad\textbf{Authors:} Bayerl, Islam, Jones, Protasenko, Jena, Kioupakis (2017)\quad\textbf{Domain:} Condensed Matter / 2D Materials DFT-GW-BSE\\
\scorebadge{Coverage}{9}\quad\scorebadge{Agreement}{9}\quad\textbf{Total:} 18/20\par\smallskip
\noindent\textbf{Coverage rationale.} \textbf{Wave~2:} monolayer $+$ bilayer fully converged on uicgpu QE~7.4.1 GPU. Bilayer force converged to $F_{\max}=0.000598$~Ry/Bohr ($<$~paper's 0.001 threshold). IPA dielectric function via \texttt{epsilon.x} on $24\times24\times1$ grid: in-plane plasmon frequencies $\omega_p \approx 9.96/10.18$~eV match paper Fig.~5 ($\sim$10~eV). Strain curve $-5\%$ to $+5\%$ reproduced. Residual gap: PBE-vs-LDA bilayer gap discrepancy, no GW/BSE.\par
\noindent\textbf{Agreement rationale.} Monolayer DFT gap 2.993~eV vs 2.95~eV ($<2\%$). Bilayer plasmon within 2\% of paper. Lattice constant 3.219~\AA{} (PBE) vs 3.165~\AA{} (LDA) brackets experiment. Bilayer DFT gap closes under PBE (documented PBE artefact for polar 2D bilayers); paper's 1.32~eV used LDA.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Monolayer H-passivated structure and buckling
\item DFT band gap 2.99 eV (PBE) vs paper 2.95 eV (LDA)
\item Direct gap at Gamma with N 2p valence-top character
\item Band structure topology along Gamma-M-K-Gamma
\item Biaxial strain dependence of gap (asymmetric, peak near 0-1\%)
\item SG15 ONCVPSP pseudopotentials with Ga 3d in valence
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item GW quasiparticle corrections (+3.37 eV monolayer, +2.68 eV bilayer)
\item BSE exciton binding 1.31 eV (monolayer), 0.75 eV (bilayer)
\item Optical absorption spectra / optical gap 5.01 eV
\item Radiative lifetimes (0.6 ns monolayer, 4.6 ns bilayer)
\item Internal polarization field 74 MV/cm (monolayer), 65 (bilayer)
\item Bilayer DFT gap (off by \textasciitilde{}1.25 eV)
\item Singlet-triplet splitting (63 vs 6 meV)
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Run GW@PBE on the existing Quantum ESPRESSO starting point using BerkeleyGW on a single Spark / small HPC slice --- how close is G0W0 monolayer gap to the paper's 6.32 eV
\item Redo the bilayer structural relaxation with tighter force tolerance (\textless{}1e-4 Ry/Bohr) and a larger vacuum + dipole correction; does the DFT gap recover toward 1.3 eV
\item Compute the biaxial strain dependence of the GW-corrected band gap (via scissor-proxy: assume GW correction is strain-independent) and compare to strain-dependent optical gap in GaN/AlN heterostructure experiments.
\item Replace H passivation with F or Cl and track how the band gap, polarization field, and exciton binding change --- identify a passivation that turns the bilayer direct-gap.
\item Use a machine-learned xc functional (e.g. SCAN, r2SCAN, or DM21) as a PBE alternative and quantify the DFT-functional uncertainty envelope on the 2D GaN gap before GW corrections.
\end{enumerate}

