\subsection{38. Joint Emulation of Earth System Model Temperature--Precipitation (fldgen v2.0)}
\textbf{OSTI:} \texttt{1578031}\quad\textbf{Authors:} Link et al.\ (2019)\quad\textbf{Domain:} Climate / Statistical Emulation\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Implemented all 8 algorithmic steps of fldgen v2.0 in Python (pattern scaling, residual computation, empirical CDF, normal quantile mapping, joint EOF/PCA, Fourier phase randomization Methods 1 \& 2, inverse quantile mapping, full-field reconstruction). Validated on synthetic ESM-like data with realistic spatial correlations and polar amplification.\par
\noindent\textbf{Agreement rationale.} All key statistical properties reproduced: spatial rank-correlation RMSE 0.056 (paper target: $\ll 0.1$), marginal KS test 100\% pass, cross-variable Spearman correlation $r=0.93$, temporal ACF MAE 0.067. Variance ratios $T=0.98$, $P=0.97$. All within paper's specified tolerances.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item All 8 fldgen v2.0 algorithm steps
\item Spatial rank-correlation RMSE 0.056
\item Marginal distribution: 100\% KS pass (T and P)
\item Cross-variable Spearman $r=0.93$
\item Temporal ACF MAE 0.067
\item Variance conservation (ratios 0.97--0.98)
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Real CMIP5 ESM output (used synthetic data)
\item R package \texttt{fldgen} comparison cell-by-cell
\item Paper's 42 actual ESM ensemble members
\item Downscaling to higher resolutions via the R package
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Apply fldgen v2.0 to actual CMIP6 HighResMIP output and compare generated ensembles against the R package cell-by-cell --- does the Python implementation match to $<1\%$ on spatial rank correlations?
\item Extend the joint state vector from $[T, P]$ to $[T, P, \mathrm{Wind}]$ --- does the Fourier phase-randomization method maintain the cross-variable correlation structure for a third variable?
\item Replace the empirical CDF with a parametric tail-extrapolation model (GPD for precipitation extremes) and measure impact on extreme-precipitation frequency in generated ensembles.
\item Use fldgen v2.0 emulator outputs as boundary conditions for a regional impact model and compare to full ESM-forced runs --- is the statistical emulator sufficient for 2$\sigma$ tail events?
\item Test whether the Phase Method 2 (phase-shift rather than random) produces more realistic temporal autocorrelation at interannual timescales compared to Method 1.
\end{enumerate}

