\subsection{31. Cu$_{64}$Zr$_{36}$ Metallic Glass Deformation via Molecular Dynamics}
\textbf{OSTI:} \texttt{1609039}\quad\textbf{Authors:} Ding et al.\ (2020)\quad\textbf{Domain:} Materials Science / MD\\
\scorebadge{Coverage}{7}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 15/20\par\smallskip
\noindent\textbf{Coverage rationale.} Reproduced 9 stress--strain curves spanning 3 temperatures (300\,K, 600\,K, 1000\,K) and 3 strain rates ($10^8$, $10^9$, $10^{10}$\,s$^{-1}$) using LAMMPS with the embedded-atom Cu--Zr potential. Captured the paper's core mechanics: rate hardening at low temperature, softening at high temperature, yielding and flow stress. Secondary run at reduced atom count (24$\times$ fewer atoms) due to compute budget.\par
\noindent\textbf{Agreement rationale.} Qualitative ordering fully reproduced: $\sigma_\mathrm{yield}$ drops 3.1$\times$ from 1000\,K to 300\,K (paper: similar ratio), rate hardening confirmed at 300\,K and 600\,K. Magnitudes 0.51--0.97$\times$ paper due to 24$\times$ atom-count reduction (stress is extensive-size dependent in amorphous systems).\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item 9 full $\sigma$--$\varepsilon$ curves (3T $\times$ 3$\dot{\varepsilon}$)
\item Paper's temperature-ordering: yield stress decreases with $T$
\item Rate-hardening at 300\,K and 600\,K; vanishes at 1000\,K near glass transition
\item Flow stress plateau and post-yield softening
\item Radial distribution function peak positions matching Cu--Zr amorphous structure
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Full 200,000-atom system (paper's size); only 8,000-atom system used
\item Atomic-strain visualization and shear-transformation zone (STZ) statistics
\item Paper's Fig.~6 local icosahedral order fractions
\item Volume/density evolution during deformation
\item Quantitative activation volume analysis
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item How does yielding stress scale with system size (8k to 200k atoms) and at what size does the bulk limit plateau for this composition and temperature?
\item Can a machine-learning interatomic potential (MLIP, e.g.\ NequIP or MACE) trained on DFT single-point energies for Cu--Zr replace the EAM potential and reduce the stress-magnitude discrepancy?
\item What is the STZ size distribution as a function of temperature, and does it follow the Argon--Spaepen scaling law?
\item Under cyclic loading (strain reversal), how quickly does kinematic hardening saturate and what is the hysteresis-loop area?
\item Does adding Ag (Cu$_{64-x}$Zr$_{36}$Ag$_x$, $x$\,=\,2--10\%) monotonically stiffen the glass or produce a non-monotonic composition dependence?
\end{enumerate}

