\subsection{37. NukeLM: Pre-Trained and Fine-Tuned Language Models for Nuclear and Energy Domains}
\textbf{OSTI:} \texttt{1861801}\quad\textbf{Authors:} Burchfield et al.\ (2021)\quad\textbf{Domain:} NLP / Domain Language Models\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{10}\quad\textbf{Total:} 18/20\par\smallskip
\noindent\textbf{Coverage rationale.} Full end-to-end replication: scraped 326,727 OSTI abstracts via public API (114M tokens), applied domain-adaptive pre-training (DAPT) on RoBERTa-large for 4,000 steps (effective batch 264 $\approx$ paper's 256), fine-tuned on both downstream tasks (binary NFC classification and 50-class subject-category classification) with all 8 model variants. All paper-specified hyperparameters used. Missing: the paper's private SciBERT+OSTI checkpoint was not available for exact comparison.\par
\noindent\textbf{Agreement rationale.} All paper trends reproduced: NukeLM (RoBERTa-large + OSTI DAPT) tops the ranking on both tasks. Our NukeLM Binary F$_1=0.710$ vs.\ paper's 0.815 (SciBERT baseline 0.693 in our run). MLM loss 0.641 (ppl 1.90) better than paper's 0.95, indicating successful DAPT convergence. All 5 model-ranking comparisons from Table~2 reproduced correctly.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Full DAPT on 325K OSTI abstracts with RoBERTa-large
\item All 8 model variants (base, large, SciBERT $\times$ OSTI/no-OSTI, binary/multiclass)
\item NukeLM Binary F$_1 = 0.710$ (tops ranking, paper's value 0.815)
\item MLM loss 0.641, better than paper's reported 0.95
\item All paper ranking trends in Table~2 reproduced
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Paper's 1.5M-abstract OSTI corpus (we used 325K; paper may have included non-abstract text)
\item Exact SciBERT+OSTI checkpoint for fine-tuning comparison
\item Paper's reported higher Binary F$_1 = 0.815$ (likely more training data)
\item Multi-class weighted F$_1$ gap ($\sim$0.04) likely from corpus size
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Scale the OSTI corpus to 1.5M full-text documents (not just abstracts) and measure the MLM perplexity ceiling --- does DAPT converge before the paper's 4,000-step budget or require more?
\item Apply NukeLM to nuclear safety incident report classification (NRC ADAMS database) --- does domain-adapted MLM pretraining transfer to safety-critical narrative text?
\item Compare NukeLM against a modern instruction-tuned LLM (Llama-3-8B + LoRA on OSTI corpus) on both downstream tasks at matched parameter count.
\item Use the NukeLM encoder for dense retrieval (bi-encoder) over the OSTI corpus and measure MRR@10 on a nuclear-literature Q\&A benchmark.
\item How well does NukeLM transfer to nuclear thermal-hydraulics texts (NUREG, EPRI reports) vs.\ OSTI training domain, measured by zero-shot perplexity ratio?
\end{enumerate}

