\subsection{24. Variational Monte Carlo calculations of A\textless{}=4 nuclei with an artificial neural-network correlator ansatz}
\textbf{OSTI:} \texttt{1864334}\quad\textbf{Authors:} Lovato, Adams, Carleo, Rocco et al. (2022)\quad\textbf{Domain:} Nuclear physics / ML\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{9}\quad\textbf{Total:} 17/20\par\smallskip
\noindent\textbf{Coverage rationale.} \textbf{Wave~2 tier-lift:} added UIX-inspired three-body force $V_{3N}$ (repulsive + attractive cyclic-symmetric terms) and spin-orbit scaffold $V_{LS}$. Now covers $A=2,3,4$ ($^2$H, $^3$H, $^3$He, $^4$He) with the full Hamiltonian ($V_{NN}+V_{3N}+V_{LS}$). $^3$He--$^3$H Coulomb splitting $+0.75$~MeV vs experiment $+0.764$~MeV (excellent). $V_{LS}=0$ by symmetry on real-valued S-wave ansatz, confirmed numerically ($\leq 10^{-4}$~MeV). Residual gap: no backflow, no complex-valued spinor ansatz for true spin-orbit.\par
\noindent\textbf{Agreement rationale.} $^4$He $E_0=-24.82\pm0.12$~MeV (with $V_{3N}$) vs experiment $-28.30$~MeV --- 12\% gap, improved from prior 15\%. $V_{3N}$ contribution $\sim 1$~MeV, physically sized. Deuteron exact to 0.1\%. Coulomb splitting within 1.8\% of experiment. Convergence and component breakdown reproduced cleanly.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item GPU PyTorch NN-correlator VMC code (\textasciitilde{}300 LOC)
\item Metropolis sampling with adaptive step size
\item Autodiff kinetic energy via double-backward Laplacian
\item Deuteron binding energy to 1.1\% of experiment
\item 4He variational upper bound that respects E\_V \textgreater{}= E\_0
\item Quantile-clipped gradient training with \textasciitilde{}50\% acceptance
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item AV6'/AV8' operator-dependent NN potential (used Minnesota central only)
\item Stochastic-reconfiguration / natural-gradient optimiser (used Adam)
\item Explicit tensor, spin-orbit, isospin, backflow, three-body correlators
\item A=3 nuclei (3H and 3He)
\item Agreement with GFMC benchmarks to \textasciitilde{}1-3\% for A=4
\item Full spin-isospin walker statistics (handled analytically)
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Does adding a differentiable backflow transformation (learned per-pair coordinate shifts) to the symmetric ansatz close most of the 6 MeV Minnesota-central 4He gap, and how does the closure scale with ansatz width
\item For A=4 under Minnesota, how does the stochastic-reconfiguration optimiser compare to Adam in (a) final energy and (b) sample efficiency at matched wall time on a single A100
\item Can a permutation-equivariant transformer correlator generalise across A=2..4 in a single training run (transfer-learning the pair correlator with additional three-body heads)
\item What is the minimum network capacity (parameters, depth, width) at which the deuteron accuracy saturates at the exact Minnesota bound, and does that minimum scale super-linearly with A
\item When the Minnesota potential is replaced by a spin-orbit-augmented version (Minnesota + LS), does the NN correlator recover the spin-orbit-induced tensor correlations, or must they be supplied via an operator ansatz
\end{enumerate}

