\subsection{19. Simple Coplanar Waveguide Resonator Mask Targeting Multiplexed Superconducting-Qubit Readout}
\textbf{OSTI:} \texttt{1983793}\quad\textbf{Authors:} (Argonne CPW mask paper) (2022)\quad\textbf{Domain:} Quantum Devices / Superconducting circuits\\
\scorebadge{Coverage}{5}\quad\scorebadge{Agreement}{7}\quad\textbf{Total:} 12/20\par\smallskip
\noindent\textbf{Coverage rationale.} Analytical results replicated: CPW impedance via conformal mapping (48.3~$\Omega$ vs 50~$\Omega$ target), 8-resonator frequency allocation 4.6--7.4~GHz, quarter-wave lengths, $Q_c$ vs coupler length. Participation ratios computed with 2D finite-difference Laplace solver (278K-point non-uniform grid, 5~nm near interfaces). Missing: paper's full 3D FEM eigenmode + driven simulations (Ansys HFSS or Palace), full mask-layout simulation with GDS, adaptive sub-nm meshing, experimental $Q_i$ measurements.\par
\noindent\textbf{Agreement rationale.} Analytical values excellent: Z within 3.4\%, C within 14\%, frequencies exact. Participation ratios: p\_MS/p\_SA = 2.09 vs paper 2.00 (excellent). Absolute p values within \textasciitilde{}2$\times$ due to 2D thin-layer approximation. Substrate participation 91.85\% vs 89\% (3\% error). p\_MA overestimated 6$\times$ --- known limitation of 2D solver near conductor edge singularity. Q\_c vs coupler length tunable over 3+ decades (matches Fig 3).\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Conformal-mapping CPW impedance formula (Z = 48.3 $\Omega$, $\epsilon$\_eff = 6.225)
\item 8-resonator frequency plan (4.6, 5.0, 5.4, 5.8, 6.2, 6.6, 7.0, 7.4 GHz)
\item Quarter-wave resonator lengths (4.06--6.54 mm)
\item Participation ratio ordering p\_MS \textgreater{} p\_SA \textgreater{} p\_MA
\item Q\_c vs coupler length monotonic decrease over 3+ decades
\item p\_MS/p\_SA ratio = 2.09 (paper: 2.00)
\item 2D FD Laplace solver with non-uniform grid
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Full 3D FEM eigenmode simulation (Ansys HFSS or Palace)
\item Driven S-parameter simulation of the 8-resonator-on-feedline chip
\item Sub-nm adaptive meshing to resolve 3 nm interface layers accurately
\item GDS mask-level layout import and simulation
\item Kinetic-inductance correction to Z
\item Experimental Q\_i measurements and TLS loss-budget fitting
\item Realistic isotropic-etch trench geometry (curved profile)
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Run the same participation analysis in Palace (AWS open-source FEM) on the published GDS mask --- do the absolute p\_MS and p\_MA values drop toward the paper's $\times$10$^3$ scale when sub-nm interface meshing is used
\item Sweep trench depth 0--300 nm in 10 nm steps --- does p\_SA decrease monotonically, and where is the diminishing-returns knee for TLS loss reduction
\item How sensitive is p\_MS/p\_SA $\approx$ 2 to center-conductor-to-gap aspect ratio s/g Sweep s $\in$ \{3,6,9,12\} m holding Z=50 $\Omega$ via g adjustment; report the ratio's $\pm$3$\sigma$ band across realistic fab tolerances.
\item Model kinetic inductance of a 100 nm Nb film with $\lambda$\_L = 80 nm and re-compute Z and f --- does the 3.4\% gap close, and do all 8 frequencies shift consistently
\item Couple the analytical Q\_c(\_c) curve to the participation-ratio loss model --- can a single scalar 'design efficiency' metric recommend an optimal coupler length that jointly minimizes TLS loss and maximizes multiplexed readout fidelity
\end{enumerate}

