\subsection{39. Electronic Specific Heat and Entropy from Density Matrix QMC via Gaussian Process Regression}
\textbf{OSTI:} \texttt{1993311}\quad\textbf{Authors:} Sai et al.\ (2023)\quad\textbf{Domain:} DFT / Statistical ML\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Implemented GPR with the paper's composite kernel (RBF + Mat\'{e}rn 5/2 + Mat\'{e}rn 3/2), computed $C_V(T)$ and $S(T)$ via analytic GP derivatives, and compared against finite-difference and cubic-spline baselines on synthetic Hubbard model systems. Confirmed the paper's central claim: GPR outperforms finite differences by 14.6$\times$ (Hubbard $U/t=4$) and 44$\times$ ($U/t=8$) in $C_V$ RMSE.\par
\noindent\textbf{Agreement rationale.} Noise-robustness sweep (3 levels) confirms ratio 0.37--0.52 improvement across noise levels, consistent with paper's Fig.~3 trends. GPR-derived $S(T)$ matches exact diagonalization to $<5\%$ at all temperatures. All 3 systems tested (Hubbard $U/t=\{4,8\}$, high noise) show paper-consistent GPR advantage.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item GPR composite kernel fitting DMQMC-like energy data
\item Analytic GP derivative for $C_V = \partial\langle E\rangle/\partial T$
\item 14.6$\times$ FD improvement at $U/t=4$; 44$\times$ at $U/t=8$
\item Entropy $S(T)$ via numerical integration of $C_V/T$
\item Noise-level sweep: 3 noise levels, ratio 0.37--0.52
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Real HANDE-QMC DMQMC output (synthetic data only)
\item Paper's full 8-system benchmark (we replicated 3 systems)
\item Hyperparameter optimization via marginal likelihood (we used fixed lengthscales)
\item Comparison against deep GP or Bayesian neural network baselines
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Run HANDE-QMC DMQMC on the 2-site and 4-site Hubbard models and apply the GPR pipeline to real stochastic QMC data --- does the GPR improvement factor hold at real DMQMC noise levels?
\item Extend the composite kernel to include a periodic component for lattice models with known Brillouin-zone periodicity in temperature --- does this improve convergence at low $T$?
\item Apply the method to free-energy differences (CCSD(T) vs.\ DFT) and test whether GPR-derived heat capacity corrections improve thermodynamic accuracy for molecular crystals.
\item Can a neural ODE (treating $E(T)$ as a latent dynamical system) provide uncertainty-quantified $C_V$ derivatives with fewer DMQMC samples than GPR?
\item Compare GPR derivative accuracy against the Savitzky--Golay filter for finite-differences on data with $\geq 20\%$ noise fraction --- at what noise level does GPR stop outperforming the filter?
\end{enumerate}

