\subsection{11. Molten Salt Reactor Neutronics and Fuel Cycle Modeling and Simulation with SCALE (MSRE Depletion)}
\textbf{OSTI:} \texttt{2217719}\quad\textbf{Authors:} Betzler, Powers, Worrall (2017)\quad\textbf{Domain:} Nuclear Engineering / Reactor Physics\\
\scorebadge{Coverage}{6}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 14/20\par\smallskip
\noindent\textbf{Coverage rationale.} Reproduced MSRE core geometry (2D axial slice, 22.5\% fuel fraction), fuel salt composition, graphite moderator, Hastelloy-N vessel, and online noble-gas/noble-metal removal rates. Used OpenMC Monte Carlo depletion with 25 steps x 15 days = 375 days. Did NOT replicate: full 3D deterministic SCALE/TRITON model, full $\sim$900-day operational history with fuel additions, or the broader fuel-cycle sensitivity studies of the paper.\par
\noindent\textbf{Agreement rationale.} Initial $k_\mathrm{eff} = 1.165 \pm 0.001$ (ours) vs $\sim$1.16 (paper SCALE) --- excellent agreement to $\sim$0.5\%. Leakage 18.1\% vs paper 15--20\% range. Reactivity decreases monotonically as expected ($\Delta k = 0.077$ over 375\,d). U-235 depletion and Pu-239 buildup match expected magnitudes.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item MSRE core geometry (hex lattice, graphite stringers, core can, reflector)
\item LiF-BeF2-ZrF4-UF4 fuel salt composition at 2.32 g/cm3, 922 K
\item Initial k\_eff \textasciitilde{}1.165 matching paper
\item Online processing rates: noble gas 4.067e-5/s, noble metal 8.667e-3/s
\item OpenMC PredictorIntegrator depletion over 375 days
\item Fuel fraction 22.5\%, leakage \textasciitilde{}18\%
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Full 3D SCALE/TRITON deterministic model with 1-group transport
\item Full \textasciitilde{}900-day operational history with fuel additions / U-235 makeup
\item Broader fuel-cycle parameter sweeps from the paper
\item Spectral comparisons (fast/thermal flux distributions)
\item Temperature feedback / void coefficient studies
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item How sensitive is the 375-day reactivity swing to the online Xe-135 removal rate --- can we quantify dk/d(lambda\_Xe) and compare to MSRE operational data
\item Extend depletion to 900 days with periodic U-235 additions matching the MSRE operational log and compare drift in k\_eff to the paper's full-history curve.
\item Swap the fuel to a thorium-bearing MSR composition (LiF-BeF2-ThF4-UF4) and compute the breeding ratio with and without online protactinium separation.
\item Perform a Monte-Carlo-vs-deterministic cross-validation by running an equivalent SCALE/TRITON model on the same 2D slice and quantifying k\_eff bias as a function of energy-group structure.
\item How does the reactivity evolution change under a 3D axial model with realistic axial power profile and graphite growth (anisotropic swelling) over 2+ years
\end{enumerate}

