\subsection{4. Exactly-Solved Model of Light-Scattering Errors in Quantum Simulations with Metastable Trapped-Ion Qubits}
\textbf{OSTI:} \texttt{2441075}\quad\textbf{Authors:} Foss-Feig, Vikas, et al. (2024)\quad\textbf{Domain:} Quantum Information / AMO\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{9}\quad\textbf{Total:} 17/20\par\smallskip
\noindent\textbf{Coverage rationale.} Complete implementation of analytic solution (Eqs. 6-10) with all four terms I, R, L, B --- including the paper's novel leakage (L) and combined (B) contributions. Five-jump-operator Lindblad master equation implemented numerically with correct factor-of-2 jump convention. Ca branching ratios (94.5\% leakage / 3.9\% Raman / 1.6\% elastic). Figures 1 (schematic), 2 (GHZ fidelity), 3 (correlations), 4 (squeezing) reproduced qualitatively. Missing: full Penning-trap 2D crystal mode computation (we used 1D chain approximation for J\_ij).\par
\noindent\textbf{Agreement rationale.} Analytic-numerical agreement at machine precision (errors 10--10$^3$ across all tested cases). Trace preservation to 5.5$\times$10, positivity to 10 --- essentially exact. All qualitative figure features correct: fidelity  with N, Postselection helps, m-body correlations decay faster than exp(-mt), $^2$  N\textasciicircum{}(-2/3) scaling with scattering floor. Quantitative figure values differ because paper's Penning-trap J\_ij differs from our 1D-chain J\_ij.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Full analytic solution Eqs. 6-10 with all four I, R, L, B components (including the paper's novel L and B terms)
\item 5-jump-operator Lindblad numerical master equation with correct factor-of-2 jump convention
\item Ca branching ratios (94.5\% leakage / 3.9\% Raman / 1.6\% elastic)
\item Selection rule: |1=|mJ=-5/2 dark under $\pi$ polarization
\item Machine-precision analytic vs numerical agreement (10--10$^3$)
\item Figure 2 GHZ-fidelity qualitative trends (N dependence, postselection gain, B-field effect)
\item Figure 3 correlation decay (faster than exp(-mt)) and perpendicular-correlation growth
\item Figure 4 spin-squeezing $^2$  N\textasciicircum{}(-2/3) with scattering floor
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Penning-trap 2D triangular-lattice ion-crystal mode structure
\item Full 3D normal-mode J\_ij computation (we used 1D chain)
\item Laser power P and beam waist w (not specified in paper)
\item Exact trap frequencies $\omega$z, $\omega$r (referenced to Ref [20])
\item GHZ fidelity fourth-order $\delta$J\_ij correction terms
\item Quantitative N-thresholds from Fig 2 match
\item Experimental validation against real Ba or Ca data
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Implement the full 2D Penning-trap equilibrium-crystal mode solver and recompute J\_ij --- do the Fig 2 fidelity crossovers match the paper's reported N\_threshold at B=0.9T and B=4.5T within 10\%
\item Extend the exact solution from $\pi$ to $\sigma$$\pm$ polarization where |1 is no longer dark --- derive new analytic expressions and quantify the fidelity penalty of losing the dark-state protection.
\item Test the exact solution against a full Lindblad simulation at N=20 (near the boundary of tractable numerics) --- does the product-form correlation factorization still agree to machine precision, or do many-body corrections emerge
\item For $^3$Ba (different branching ratios, \textasciitilde{}70\% leakage), do the novel L and B terms still dominate the error budget, and does postselection recover the same 5.5\% residual-error advantage
\item Combine the exact scattering model with realistic single-qubit gate errors (miscalibration, Stark shifts) to produce a full end-to-end error budget for a 50-qubit GHZ preparation circuit --- at what N does gate error overtake scattering as the dominant error source
\end{enumerate}

