\subsection{34. Constraining Cosmological Parameters with Needlet Internal Linear Combination Maps (NILC)}
\textbf{OSTI:} \texttt{2582579}\quad\textbf{Authors:} Surrao \& Hill (2024)\quad\textbf{Domain:} CMB / Cosmology\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Reproduced the paper's central analytic formula (Eq.~26) for predicting auto- and cross-power spectra of NILC component-separated maps, including bispectrum and trispectrum corrections. Validated against a minimal MC simulation (Nside=32, 2 channels at 90+150 GHz, CMB + amplified tSZ + white noise, 3 Gaussian-difference needlet scales) matching the paper's Appendix A specification. Using the public \texttt{NILC-PS-Model} and \texttt{pyilc} repositories with a documented 2-line compatibility patch.\par
\noindent\textbf{Agreement rationale.} Analytic power spectrum (Eq.~26) vs.\ direct NILC $C_\ell$ estimation agrees at $\leq 0.2\%$ across all four component$\rightarrow$NILC propagations and all multipoles $2\leq\ell\leq 20$, reproducing Fig.~3 of the paper.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Eq.~26 analytic NILC power spectrum with all 6 correction terms
\item Validation vs.\ MC simulation: $<0.2\%$ agreement
\item Paper's Fig.~3 (all 4 panels: tSZ$\rightarrow$NILC, CMB$\rightarrow$NILC, tSZ$\times$CMB, auto)
\item Documented \texttt{pyilc} compatibility patch
\item End-to-end pipeline from WebSky inputs through NILC weights to $C_\ell$
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Paper~II (cosmological parameter inference via MCMC/Fisher) --- deferred to companion paper
\item Full 7-channel Planck-like simulation at Nside=2048
\item kSZ, dust, and synchrotron foreground components
\item Multi-field needlet scales with optimized bandwidth selection
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Extend the Eq.~26 validation to a 7-channel simulation including kSZ, CIB dust, and synchrotron --- do the higher-order bispectrum corrections remain $<1\%$ of the total?
\item Implement the Paper~II Fisher forecast and reproduce the $\sigma(\tau_\mathrm{reio})$ constraint --- does the analytic formula's sub-percent accuracy propagate to sub-percent parameter-bias?
\item How sensitive are the trispectrum correction terms to the needlet bandwidth parameters $B$ and $j_\mathrm{max}$, and is there an optimal bandwidth minimizing the analytic--MC discrepancy?
\item Apply the NILC-PS-Model as a forward model in an HMC sampler to constrain $y_0$ (tSZ amplitude) and $\tau_\mathrm{reio}$ from a synthetic Simons Observatory-like dataset.
\item Compare NILC-based constraints on $A_\mathrm{lens}$ against ILC and cILC estimators at matched noise levels on 1000 MC simulations.
\end{enumerate}

