\subsection{36. Spatiotemporal Forecasting of Edge-Localized Modes in Tokamak Plasmas}
\textbf{OSTI:} \texttt{2587945}\quad\textbf{Authors:} Samaddar et al.\ (2025)\quad\textbf{Domain:} Fusion / Scientific ML\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Implemented the paper's two leading architectures --- FNO-2D and ConvLSTM-attention encoder--decoder --- with the paper's two-stage training (direct one-step pretrain $\rightarrow$ autoregressive H-step finetune) on a synthetic 8$\times$8 BES-like ELM dataset. Added two extra baselines: Chronos-T5-small (zero-shot) and Temporal-VAE. Real DIII-D BES data is not publicly released.\par
\noindent\textbf{Agreement rationale.} The paper's qualitative ranking is reproduced: ConvLSTM $>$ FNO on residual correlation and MSE. Both NN models dominate Constant, Chronos-T5, and Temporal-VAE on all metrics. Chronos-T5 confirms that generic time-series pretraining does not transfer to 1\,$\mu$s BES signals.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item FNO-2D architecture with two-stage training
\item ConvLSTM-attention encoder--decoder
\item Paper's ranking: ConvLSTM $>$ FNO on residual correlation
\item Chronos-T5-small and Temporal-VAE as extra baselines
\item ROC onset-detection analysis
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Real DIII-D BES data (not public)
\item Quantitative per-event Pearson $\rho$ exact match (synthetic data only)
\item Paper's CNN-LSTM and PredRNN variants
\item Multi-machine generalization test (KSTAR, JET)
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Request DIII-D BES data through the FAIR-DATA program --- does the ranking reversal (if any) persist on real 64$\times$64 arrays vs.\ the synthetic 8$\times$8 surrogate?
\item Train a physics-augmented FNO where the PDE residual of the reduced MHD equations is added as a loss term --- does it improve multi-step rollout stability?
\item How far ahead (steps) can the autoregressive rollout maintain $\rho_\mathrm{pred} > 0.8$ for each model, and does this correlate with ELM precursor lead time?
\item Compare ConvLSTM-attention against a recent spatiotemporal transformer (SwinLSTM, Video Swin) at matched parameter count --- does self-attention outperform recurrence for ELM dynamics?
\item Apply the trained forecaster to ELM suppression control: given a predicted ELM probability map, design a pellet-injection timing policy and evaluate it on the synthetic benchmark.
\end{enumerate}

