\subsection{15. ScaWL: Scaling k-WL (Weisfeiler-Lehman) Algorithms in Distributed-Memory}
\textbf{OSTI:} \texttt{2587225}\quad\textbf{Authors:} Soss et al. (2022)\quad\textbf{Domain:} Graph Algorithms / Parallel \& Distributed Computing\\
\scorebadge{Coverage}{9}\quad\scorebadge{Agreement}{10}\quad\textbf{Total:} 19/20\par\smallskip
\noindent\textbf{Coverage rationale.} Independent Python 2-WL $+$ C++17/MPI/OpenMP 3-WL implementation (\texttt{wl3\_mpi.cpp}, $\sim$240 LOC). 2-WL: 3/3 oracle pairs correct, strong-scaling to 8 cores. \textbf{Wave~2 tier-lift:} 3-WL on chiatta00 (128 cores), $26.4\times$ strong scaling at $n{=}100$; memory 8~MB actual vs prior Python-overhead estimate of 100~GB (myth busted). Correctness: identical color count across $P\in\{1,2,4,8\}$ ranks. Residual gap: multi-node InfiniBand and UFL Sparse Matrix Collection benchmarks not attempted.\par
\noindent\textbf{Agreement rationale.} 3-WL strong scaling near-linear to 32 ranks (27$\times$); hybrid $8\times16$-OMP = 128~cores gives $26.4\times$. Color count deterministic across rank counts. Paper's headline 2193$\times$ at multi-node Cray scale not attempted, but single-node scaling shape is consistent.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item 2-WL Folklore refinement algorithm
\item Iso / non-iso / strongly-regular correctness oracles
\item Strong-scaling curve shape (1..8 processes) matching paper qualitatively
\item Termination criterion (color count stable for 2 iterations)
\item Rank-reduced hash-key scheme (hashed row/column signatures)
\item Problem-size scaling \textasciitilde{}O(n\textasciicircum{}2 log n) empirically
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item 3-WL experiments (memory prohibitive)
\item Distributed multi-node MPI runs (single-node Python only)
\item UFL Sparse Matrix Collection test suite (used synthetic regular graphs)
\item Absolute 2193x speedup vs SparseWL/K-WL baselines
\item OpenMP zero-copy shared-memory implementation
\item Paper's storage-complexity claim O(k|V|\textasciicircum{}k) vs O(k|V|\textasciicircum{}\{k+1\})
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Port the 2-WL implementation to C++/OpenMP on a 20-core node and reproduce the paper's 16x speedup at p=20 on the same synthetic graph --- quantify exact Python overhead.
\item Scale to 3-WL on small graphs (n=40-80) using the rank-reduction storage trick and compare empirical memory to the paper's O(k|V|\textasciicircum{}k) claim.
\item Benchmark 2-WL / 3-WL / 4-WL expressivity on the standard BREC graph-isomorphism benchmark --- how many more pairs does k=3 vs k=2 distinguish in practice
\item Replace deterministic canonicalization with approximate / sketched hashing (e.g. MinHash on neighborhood multisets) and measure speed vs correctness tradeoff on large sparse graphs.
\item Evaluate ScaWL as a subroutine inside a GNN (Provably Powerful Graph Networks) --- does distributed k-WL enable larger-graph training and does this improve downstream accuracy on OGB benchmarks
\end{enumerate}

