\subsection{35. Mesh-Based Super-Resolution of Fluid Flows with Multiscale GNN}
\textbf{OSTI:} \texttt{2587579}\quad\textbf{Authors:} Barwey et al.\ (2025)\quad\textbf{Domain:} PDE / Scientific ML\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Directly used the authors' open-source \texttt{DDP\_PyGeom} code. Reproduced the headline distributed halo-swap mechanism (the paper's primary technical contribution), validated it bitwise across 3 rank configurations, and trained the multiscale UNet-GNN on 2D and 3D spectral-element meshes. 4.77$\times$ rel-L$^2$ reduction over interpolation baseline in 2D; 1.11$\times$ in 3D (limited run).\par
\noindent\textbf{Agreement rationale.} The distributed-sync validation is the paper's core claim: halo exchange over coincident nodes reproduces single-rank reference to $\leq 5.4\times10^{-9}$ rel-L$^2$, confirming bitwise equivalence. 2D superresolution factor agrees with paper's reported range. 3D factor modest due to limited training budget.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Multi-rank halo-swap validated bitwise vs.\ single-rank (rel L$^2 \leq 5.4\times10^{-9}$)
\item 2D Chebyshev spectral-element mesh: 4$\times$4 elements at $p=7$
\item 3D hexahedral SE mesh: 4$\times$2$\times$2 at $p=5$; backward-facing step flow
\item 4.77$\times$ rel-L$^2$ reduction over trilinear interpolation (2D)
\item 305k-param 2D model, 682k-param 3D model (hidden=96)
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Full-scale turbulent combustion NekRS results (Table~2 paper)
\item Multi-GPU distributed training at $\geq$4 ranks with NCCL (NCCL Xid74 blocked on test system)
\item Quantitative comparison vs.\ polynomial interpolation at high $p$
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Scale training to 8 GPUs using NCCL on Polaris and measure strong-scaling efficiency of the halo-swap barrier --- does it remain $<5\%$ of iteration time at 8 ranks?
\item Compare the multiscale GNN against a FNO (Fourier Neural Operator) on the same SE meshes --- which transfers better from $p=7$ training to $p=9$ inference?
\item Does the superresolution factor improve monotonically with GNN depth, or is there an optimal depth/width for SE mesh structure?
\item Apply the model to pressure super-resolution in a turbulent channel flow DNS at $\mathrm{Re}_\tau=550$ and measure recovery of the pressure--velocity cross-spectrum.
\item Can the halo-swap mechanism be extended to non-conforming mesh interfaces (hanging nodes) without breaking the bitwise distributed equivalence guarantee?
\end{enumerate}

