\subsection{14. Spin-Dependent Scattering of Sub-GeV Dark Matter}
\textbf{OSTI:} \texttt{3014512}\quad\textbf{Authors:} Gori, Knapen, Lin, Munbodh, Suter (2025)\quad\textbf{Domain:} Particle Physics / Dark Matter Direct Detection\\
\scorebadge{Coverage}{7}\quad\scorebadge{Agreement}{7}\quad\textbf{Total:} 14/20\par\smallskip
\noindent\textbf{Coverage rationale.} Reproduced full rate machinery via DarkELF for three mediator operators (phi, a, A') across Al2O3 and GaAs, covering DM masses 1 MeV--1 GeV and thresholds 1 meV--1 eV. Reproduced paper Figs. 5--8 (phonon DOS + three mediator reach plots) plus SD vs SI comparison. Missing: constraint plots (Figs 1--4) from SN/SIDM/LHC, Figs 9--10 optimized-mediator-mass scan, experimental exclusions overlays.\par
\noindent\textbf{Agreement rationale.} Reference sigma values for Al2O3/A'/heavy/1meV at m\_chi\textasciitilde{}100 MeV: 1.9e-40 cm\textasciicircum{}2 (ours) consistent with paper's Fig. 8 within 10--20\% digitization uncertainty. Operator hierarchy (a \textless{} phi \textasciitilde{} A'), target hierarchy (Al2O3 \textgreater{} GaAs), SD/SI ratio \textasciitilde{}10\textasciicircum{}3--10\textasciicircum{}4 all reproduced. GaAs normalization off by \textasciitilde{}5--10x vs paper (partial mismatch in nuclear matrix elements). 31/31 unit tests pass.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item DarkELF multiphonon SD rate computation for phi, a, A' operators
\item Standard Halo Model parameters (v0=220, ve=240, vesc=500 km/s, rho\_chi=0.4)
\item Figure 5 (Al2O3, GaAs phonon partial DOS)
\item Figure 6 (phi mediator reach) for both targets, heavy/light
\item Figure 7 (a mediator) with q\textasciicircum{}5 integrand behavior
\item Figure 8 (A' mediator, m\_A' = 10 GeV)
\item SD vs SI 10\textasciicircum{}3-10\textasciicircum{}4 gap
\item Isotope spin factors for 27Al, Ga-69/71, As-75
\end{itemize}\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Figures 1-4 (mediator constraints: SN cooling, meson decays, SIDM, LHC)
\item Figures 9-10 (optimized mediator mass scan per m\_chi)
\item Experimental exclusion overlays (PICO, CRESST, CDEX)
\item Massless-mediator SI benchmark
\item Full absolute calibration of GaAs rate vs paper (off 5-10x)
\end{itemize}\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item How does the SD reach for Al2O3 change if realistic experimental resolution (sigma\_E \textasciitilde{} 0.5 meV TES) and backgrounds are folded into the 1 meV threshold curves
\item Run the DarkELF computation on a wider target panel (sapphire, GaN, diamond, ZnO, Si3N4) at 1 meV threshold and rank candidates by SD reach per kg$\cdot$yr for each operator.
\item Produce the missing Figs. 9-10 by scanning m\_med over [0.1, 10]*q\_0 per m\_chi and constructing the envelope minimum-sigma curve; quantify how much reach improves vs fixed m\_med=3q\_0.
\item For the A' model, fold in the realistic SN+SIDM constraint band (from the paper's Figs. 1-4) and identify the residual DM-mass window where Al2O3 at 1 meV can make a world-leading statement.
\item Compare the DarkELF single-phonon vs multi-phonon+impulse transition by checking the crossover energy and cross-section continuity at E\_th \textasciitilde{} phonon bandwidth for Al2O3.
\end{enumerate}

