\subsection{42. Box Least Squares Transit Detection (Kovács/Zucker/Mazeh 2002 + Hartman/Bakos 2016)}
\textbf{OSTI:} (A\&A 2002 / A\&C 2016, no OSTI)\quad\textbf{Authors:} Kovács, Zucker \& Mazeh (2002); Hartman \& Bakos (2016)\quad\textbf{Domain:} Astrophysics / Exoplanets\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Implemented the BLS algorithm from scratch (KZM02 Eqs.~3--6), including the Hartman--Bakos phase-binning optimization ($n_b=300$ bins, $O(N n_b)$ inner loop via cumulative sums). Validated on 6 Kepler targets spanning 0.84--3.55\,d periods and 150--16,000\,ppm depths.\par
\noindent\textbf{Agreement rationale.} All 6 Kepler planet periods recovered to $<0.012\%$ error. Mean period accuracy 0.007\% vs.\ astropy \texttt{BoxLeastSquares} 0.026\%. SDE $>23$ for all targets; Kepler-10\,b (150\,ppm, 0.84\,d) successfully detected.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item BLS SR statistic (KZM02 Eq.~3--6) with inverse-variance weights
\item Phase-binning speedup (Hartman--Bakos 2016)
\item All 6 Kepler planet periods to $<0.012\%$ error
\item Kepler-10\,b detection at 150\,ppm, 0.84\,d
\item Beats astropy mean accuracy by $3.7\times$
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Multi-planet deblending (iterative BLS subtraction)
\item Frequency-grid density optimization for non-uniform sampling
\item GPU-parallelized period grid search
\item Validation on TESS 2-min cadence data
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Implement the BLS-based multi-planet search (iterative signal subtraction) and validate on Kepler multi-planet systems (Kepler-11, Kepler-90) --- how many additional planets are recovered vs.\ single-pass BLS?
\item Compare BLS against the Transit Least Squares (TLS; Hippke \& Heller 2019) algorithm on a synthetic population of 1,000 injected transits across noise levels from 10 to 5000\,ppm.
\item Port the inner period loop to CUDA using CuPy and measure the GPU speedup for the TESS full-frame image cadence (2\,min, 10$^6$ stars) --- is BLS the throughput bottleneck?
\item Apply the BLS pipeline to TESS CVZ data for a solar-type star and attempt to detect sub-Earth-radius transits ($R_p < 1 R_\oplus$) via detrending + binned BLS.
\item Characterize BLS false-positive rate on stellar variability (spots, eclipsing binaries) for the Kepler DR25 sample and compare against the paper's SDE threshold of 7.
\end{enumerate}

