\subsection{64. \textit{Lactiplantibacillus plantarum} DJF10 Probiotic Genome}
\textbf{DOI:} 10.3389/fmicb.2022.823145\quad\textbf{Authors:} Kandasamy et al.\ (2022, \textit{Frontiers in Microbiology})\quad\textbf{Domain:} Probiotic Genomics / Safety Assessment\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{9}\quad\textbf{Total:} 17/20\par\smallskip
\noindent\textbf{Coverage rationale.} SPAdes de-novo assembly from SRA reads (SRR14598288) on uicgpu yielded 3{,}382{,}068\,bp / GC 44.29\% / 3{,}169 CDS — essentially exact match vs.\ paper's 3{,}385{,}113\,bp / 44.3\% / 3{,}168 CDS (\textbf{$\Delta$ = 0.09\%}). Full safety/probiotic-trait inventory recovered: 0 AMR genes across 3 databases (CARD, NCBI AMRFinderPlus, ResFinder), 0 virulence factors across 3 databases (VFDB, PathoFact, Virulence Finder), 0 plasmid replicons. 5 cold shock proteins exactly matched, bile salt hydrolase 99.7\% identity, complete sugar-utilization gene complement.\par
\noindent\textbf{Agreement rationale.} 79\% of testable claims fully verified, just below the 80\% REPLICATED threshold. Six claims rely on web-only tools without reliable CLI/API alternatives: PHASTER (prophage), RAST (subsystems), KEGG BlastKOALA (functional categories), BAGEL4 (bacteriocins), IslandViewer (genomic islands), dbCAN (CAZyme). These web-only blockers gate the remaining coverage.\par\smallskip
\noindent\textbf{Verdict: PARTIAL.} Genome assembly + safety profile reproduce exactly; further claims gated by web-only annotation tools.
