\subsection{67. Vancomycin-Resistant \textit{Enterococcus faecium} in Latin America}
\textbf{DOI:} 10.3389/fmicb.2020.01831\quad\textbf{Authors:} R\'{i}os et al.\ (2020, \textit{Front.\ Microbiol.})\quad\textbf{Domain:} Genomic Epidemiology / VREfm Phylogeography\\
\scorebadge{Coverage}{9}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 17/20\par\smallskip
\noindent\textbf{Coverage rationale.} Full 55/55 LATAM VREfm genome panel processed: Prokka annotation, MLST, abricate AMR profiling, Roary pan-genome (1{,}657 single-copy core genes $\to$ 1{,}575{,}750\,bp concatenated alignment), FastTree GTR+$\Gamma$ on 46{,}465 SNP sites, ClonalFrameML for recombination. 11/15 testable claims fully tested; 4 NOT\_TESTED with documented infeasibility (Bayesian molecular clock dating via BEAST MCMC on 340-genome global panel: days-to-weeks of compute, beyond replication budget).\par
\noindent\textbf{Agreement rationale.} 8 VERIFIED + 3 PARTIAL of 11 testable claims; 0 contradicted. MLST profile exact (ST17~=~18 genomes, ST412~=~21), vanA in 54/55 (paper: 54/55), two-clade structure with 92.6\% concordance to paper's CRS-I/CRS-II assignments, no geographic clustering, earliest LATAM VREfm (ERV1, Colombia 1998, ST17) confirmed. Partial: core genome 2{,}068 orthogroups (paper: 1{,}674, Prokka-vs-RAST annotation difference); pan-genome 6{,}441 (paper: 6{,}735, 95.6\% agreement); recombination 22.7\% (paper: 54\%, smaller core-only dataset).\par\smallskip
\noindent\textbf{Verdict: PARTIAL.} Core epidemiology robustly reproduced; molecular dating claims correctly flagged as compute-infeasible.
