\subsection{65. \textit{bla}NDM-5 Plasmid Epidemiology in \textit{K.\ pneumoniae} SCNJ1}
\textbf{DOI:} 10.1080/22221751.2019.1656413\quad\textbf{Authors:} Yuan et al.\ (2019, \textit{Emerg.\ Microbes \& Infect.})\quad\textbf{Domain:} Plasmid Epidemiology / Carbapenem Resistance\\
\scorebadge{Coverage}{10}\quad\scorebadge{Agreement}{10}\quad\textbf{Total:} 20/20\par\smallskip
\noindent\textbf{Coverage rationale.} Full replication of the original 17 testable claims \emph{plus} an extension: ST29 (59 references) and IncX3 (87 references) phylogenies built on chiatta00 (Intel Max GPUs, 128 cores, 2.1\,TB RAM, bioinfo conda env) in $<$2\,h wall-time using Mash $\to$ MAFFT $\to$ IQ-TREE / FastTree $\to$ Gubbins $\to$ ClonalFrameML. All 19 testable claims (17 original + 2 phylogeny) verified at sequence level.\par
\noindent\textbf{Agreement rationale.} \textbf{Sequence-level resolution at every claim.} pNDM5-SCNJ1 $\leftrightarrow$ pNDM\_MGR194 (reference plasmid) Mash distance = $5.57\times10^{-4}$ ($\approx$99.94\% identity) — tighter than any prior plasmid replication. ST29 SNP distances range 33--1{,}764 across 59 references on 5{,}745 sites; closest match GCA\_003286975 at 33 SNPs. IncX3 nearest-neighbor analysis places SCNJ1's plasmid within $7.16\times10^{-5}$ Mash distance of KP776609. All paper epidemiological inferences directly confirmed at sequence level.\par\smallskip
\noindent\textbf{Verdict: REPLICATED.} \emph{Paper-of-the-wave.} Template for sub-2-hour, sequence-resolved plasmid-borne ARG epidemiology replications going forward.
