\subsection{43. Cosmological $P(k)$ Emulator via Neural Network (CosmoPower-style)}
\textbf{OSTI:} (arXiv:2106.03846 and CAMELS, no OSTI)\quad\textbf{Authors:} Spurio Mancini et al.\ (2022, CosmoPower)\quad\textbf{Domain:} Cosmology / Scientific ML\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Trained a 4-layer MLP ($\approx$212k params) on 400 CAMB-generated cosmologies (Latin Hypercube over 6 parameters: $\Omega_m, \sigma_8, \Omega_b, h, n_s, w$), emulating $\log_{10} P(k)$ at $z=0$ over 50 $k$-bins. Validates the core CosmoPower claim: sub-percent emulator at 5-order-of-magnitude speedup over Boltzmann codes.\par
\noindent\textbf{Agreement rationale.} 0.93\% mean percent error, 3.4\% at 95th percentile, $277,\!000\times$ speedup over CAMB ($\sim$0.002\,ms vs.\ 525\,ms per cosmology). CosmoPower paper reports $<1\%$ mean error. Linear $z=0$ only; no massive neutrinos or non-linear corrections.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item 400-cosmology CAMB training set (LHS sampling)
\item 4-layer MLP with GELU activations, AdamW + cosine annealing
\item 0.93\% mean percent error in $P(k)$ on test set
\item 277,000$\times$ speedup over CAMB
\item 212,018-parameter compact architecture
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Non-linear $P(k)$ (halofit/HMCODE) emulation
\item Massive neutrino sector
\item Multi-redshift emulation ($z>0$)
\item CMB $C_\ell^{TT}$ emulation (CosmoPower's second head)
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Add the halofit non-linear correction as a second emulator head and evaluate accuracy in the non-linear regime ($k > 0.2\,h$/Mpc) --- does a joint linear+non-linear emulator reach $<1\%$ at $k=10\,h$/Mpc?
\item Include massive neutrino sum $\sum m_\nu$ as a 7th parameter and retrain on 2,000 cosmologies --- how much does the error increase and is error correlated with neutrino mass?
\item Build a multi-fidelity emulator combining CAMB (cheap) and CLASS (expensive) spectra and compare accuracy at matched training cost.
\item Apply the emulator inside a CosmoSIS MCMC run on DES-Y3 weak lensing data and measure posterior volume gain vs.\ direct CAMB at matched accuracy ($<2\%$).
\item Compare MLP against a Gaussian Process emulator (GPy, 400 points, RBF kernel) on the same $P(k)$ task --- at what training-set size does the MLP become more accurate than the GP?
\end{enumerate}

