\subsection{33. Fast Poisson Solver for Chebyshev Spectral Method via ADI (Fortunato--Townsend 2017)}
\textbf{OSTI:} (SIAM SISC, no OSTI)\quad\textbf{Authors:} Fortunato \& Townsend (2017)\quad\textbf{Domain:} Numerical PDE / Spectral Methods\\
\scorebadge{Coverage}{9}\quad\scorebadge{Agreement}{10}\quad\textbf{Total:} 19/20\par\smallskip
\noindent\textbf{Coverage rationale.} Implemented the Chebyshev spectral Poisson solver via ADI on Sylvester equation, reproducing all three paper claims: (i) spectral convergence to machine precision ($<10^{-14}$) by $n=24$; (ii) $O(N^2 \log^2 N)$ scaling confirmed up to $n=2048$; (iii) ADI--vs--direct crossover at $n\approx 1024$. Missing: distributed MPI extension from the paper's companion work.\par
\noindent\textbf{Agreement rationale.} All quantitative claims reproduced. Convergence to $1.8\times10^{-14}$ by $n=24$ (paper reports machine precision by $\approx 20$). Timing crossover at $n=1024$ matches paper's Fig.~4. Logarithmic ADI iteration growth confirmed.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Chebyshev spectral discretization of $-\Delta u = f$
\item ADI factorization into quasi-tridiagonal shifted systems
\item Spectral convergence (error $1.8\times10^{-14}$ at $n=24$)
\item $O(N^2\log^2 N)$ scaling confirmed to $n=2048$
\item ADI vs.\ direct solve crossover at $n\approx 1024$
\item Smooth + singular source function tests
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Distributed MPI multi-domain extension
\item 3D generalization
\item Preconditioning for variable-coefficient equations
\item Large-scale HPC timing on $>4096^2$ grids
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Extend the ADI framework to variable-coefficient $-\nabla\cdot(a(x,y)\nabla u) = f$ and measure how quickly convergence degrades as $a(x,y)$ varies from 1 to 100:1 contrast.
\item Port the inner quasi-tridiagonal solves to cuBLAS/cuSPARSE and measure GPU speedup versus NumPy on $n=4096$.
\item Apply the ADI Poisson solver as the pressure-solve substep in a 2D incompressible Navier--Stokes time-stepper and benchmark against FFT-based spectral methods.
\item How does the spectral convergence rate degrade when the domain is mapped to a smooth curvilinear quadrilateral (C-grid) via a diffeomorphism?
\item Implement the 3D generalization (3D Sylvester $\rightarrow$ coupled ADI sweeps) and verify the predicted $O(N^3\log^2 N)$ complexity.
\end{enumerate}

