\subsection{41. NANOGrav 15-Year Stochastic Gravitational-Wave Background Evidence}
\textbf{OSTI:} (ApJL 2023, arXiv:2306.16213)\quad\textbf{Authors:} Agazie et al.\ NANOGrav Collaboration (2023)\quad\textbf{Domain:} Astrophysics / Gravitational Waves\\
\scorebadge{Coverage}{8}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 16/20\par\smallskip
\noindent\textbf{Coverage rationale.} Used the official NANOGrav DR3 public data (67 pulsars, presampled MCMC chains, precomputed optimal statistic results). Recovered all key reported quantities: GWB amplitude, spectral index, Hellings--Downs spatial correlations, MCOS SNR, free-spectrum shape, and HD vs.\ CURN/monopole/dipole model comparison.\par
\noindent\textbf{Agreement rationale.} $\gamma = 3.35$ vs.\ paper's 3.2 (within $0.5\sigma$); $\log_{10}A = -14.17$ vs.\ $-14.19$ (within $0.2\sigma$); MCOS SNR $= 2.94\sigma$ vs.\ paper's $\sim 3\sigma$. All reported claims reproduced within uncertainties.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item $\log_{10}A = -14.17 \pm 0.10$ (paper: $-14.19$)
\item Spectral index $\gamma = 3.35$ (paper: $\sim 3.2$, $0.5\sigma$ consistent)
\item MCOS HD SNR $= 2.94\sigma$ (paper: $\sim 3\sigma$)
\item HD correlation pattern vs.\ monopole/dipole alternatives
\item Free-spectrum power at 30 frequency bins
\item HD vs.\ CURN Bayes factor from hypermodel chain
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Full Bayesian inference from raw TOAs (used presampled chains)
\item Noise parameter sampling for all 67 pulsars (697 parameters)
\item Alternative ORF model fits (monopole ORF posterior)
\item Follow-up 18-yr dataset comparison
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Rerun the CURN vs.\ HD hypermodel with \texttt{enterprise} from raw TOA data for the brightest 10 pulsars --- does the restricted subset still yield $>2\sigma$ HD preference?
\item Fit the free-spectrum data with a broken power law to test whether the spectral turnover suggested in the 18-yr preliminary data is present in the 15-yr set.
\item Add the 2023--2025 NANOGrav timing residuals (18-yr dataset) to the DR3 chains via Gibbs update and estimate the significance improvement.
\item Compare the SMBHB interpretation against a cosmic string network interpretation by fitting both models to the free-spectrum posterior --- which achieves lower DIC?
\item Apply the MCOS framework to the 67-pulsar set with a non-GR polarization tensor (scalar-transverse, vector-longitudinal) and place upper limits on beyond-GR modes.
\end{enumerate}

