\subsection{59. Domain-Decomposition Preconditioning for PINNs (Kopani\'cakov\'a et al.\ SIAM J.~Sci.~Comput.\ 2023)}
\textbf{arXiv:} \texttt{2306.17648}\quad\textbf{Authors:} Kopani\'cakov\'a, Kothari, Karniadakis, Krause (2023)\quad\textbf{Domain:} ML / PDE / Optimization\\
\scorebadge{Coverage}{7}\quad\scorebadge{Agreement}{7}\quad\textbf{Total:} 14/20\par\smallskip
\noindent\textbf{Coverage rationale.} 3 of 4 test cases complete (Klein-Gordon, Burgers, Allen-Cahn); advection-diffusion partially tested (MSPQN only). 15/18 claims evaluated (83\%). Sensitivity study (subdomain count $\times$ local iterations) performed for Klein-Gordon. Architecture exactly matched: ResNet PINN with adaptive tanh, Xavier init. \textbf{Key gap:} The paper's custom L-BFGS optimizer (cubic backtracking + strong Wolfe conditions) is not publicly available; PyTorch L-BFGS and scipy L-BFGS-B were used as substitutes.\par
\noindent\textbf{Agreement rationale.} Core algorithmic contribution confirmed: MSPQN achieves 5--44$\times$ lower loss than standard L-BFGS across all tested problems. Klein-Gordon: MSPQN achieves $E_{\mathrm{rel}}$=3.85$\times 10^{-3}$ vs L-BFGS $E_{\mathrm{rel}}$=5.65$\times 10^{-2}$ (14.7$\times$ improvement), 42$\times$ faster. Sensitivity predictions hold: $n_{\mathrm{sd}}$=4, $k_s$=100 optimal. \textbf{Quantitative gap:} Absolute $E_{\mathrm{rel}}$ values $\sim$100$\times$ higher than paper's ($\sim$10$^{-2}$ vs paper's $\sim$10$^{-4}$), attributable to the missing custom optimizer.\par\smallskip
\noindent\textbf{Key findings:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item Schwarz-preconditioned quasi-Newton (SPQN) consistently improves PINN training convergence---the core contribution is sound
\item MSPQN (multiplicative) outperforms ASPQN (additive) on single GPU
\item L-BFGS stagnation on advection-diffusion confirmed (both methods stall)
\item The custom L-BFGS optimizer is the critical missing piece for quantitative reproduction
\end{itemize}
\noindent\textbf{Verdict: PARTIAL.} Relative improvements confirmed; absolute accuracy values not matched due to unavailable optimizer code.
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Implement cubic backtracking line search with strong Wolfe conditions in PyTorch---does this close the 2-OOM gap in absolute $E_{\mathrm{rel}}$?
\item Can SPQN preconditioning be combined with Adam (instead of L-BFGS) as the global smoother? This would avoid the L-BFGS implementation sensitivity entirely.
\item Benchmark SPQN against modern PINN training techniques (causal weighting, curriculum learning, multi-fidelity) on the same 4-problem suite.
\item Does ASPQN achieve speedup on multi-GPU (the paper's claimed 28--39$\times$)? Implement truly parallel subdomain solves on 4$\times$A100.
\item Apply SPQN to a real-world PDE (e.g., Navier--Stokes at moderate Re) rather than the paper's 1D/2D benchmarks---does the preconditioning advantage hold?
\end{enumerate}

