\subsection{44. Poisson Flow Generative Models (PFGM; Xu et al.\ 2022 NeurIPS)}
\textbf{OSTI:} (NeurIPS 2022, arXiv:2209.11178)\quad\textbf{Authors:} Xu, Liu, Tegmark \& Jaakkola (2022)\quad\textbf{Domain:} ML / PDE-inspired Generative Modeling\\
\scorebadge{Coverage}{7}\quad\scorebadge{Agreement}{8}\quad\textbf{Total:} 15/20\par\smallskip
\noindent\textbf{Coverage rationale.} Implemented PFGM from scratch: training (Algorithm~1, augmented-space Poisson field, MSE on normalized field) and sampling (Eq.~6, backward ODE with log-$z$ change of variable, exact prior sampling for $N=2$). Added a Variance-Exploding diffusion baseline at matched capacity. Validated on 8-mode Gaussian mixture in 2D. Image-generation benchmarks (CIFAR-10, CelebA) skipped due to compute budget.\par
\noindent\textbf{Agreement rationale.} PFGM SWD 0.049 vs.\ diffusion 0.059 on the 2D toy task; PFGM 1.2--1.4$\times$ more step-size robust at 20--50 NFE. Perfect 8/8 mode coverage. Reproduces the paper's qualitative claim: PFGM outperforms diffusion on 2D and is more robust to step size.\par\smallskip
\noindent\textbf{What reproduced:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item PFGM training Algorithm~1 with augmented-space field target
\item Backward ODE sampling with log-$z$ change of variable
\item Exact prior sampling from $p_\mathrm{prior}(x)$ for $N=2$
\item VE diffusion baseline (probability flow ODE)
\item PFGM SWD 0.049 vs.\ diffusion 0.059 (8-mode MoG, 2D)
\item 8/8 mode coverage for both models
\item Step-size robustness: PFGM 1.2--1.4$\times$ at 20--50 NFE
\end{itemize}
\noindent\textbf{What missing:}
\begin{itemize}[leftmargin=1.4em,itemsep=0.2em,topsep=0.2em]
\item CIFAR-10 and CelebA image benchmarks (FID scores)
\item PFGM++ extension (higher-dimensional Poisson field)
\item Score-function baseline comparison at equal NFE budgets
\item GPU-scale training on high-resolution images
\end{itemize}
\noindent\textbf{Follow-on research questions:}
\begin{enumerate}[leftmargin=1.6em,itemsep=0.2em,topsep=0.2em,label=Q\arabic*.]
\item Train PFGM on CIFAR-10 with an NCSN++ architecture and compare FID at $N_\mathrm{FE}=\{20, 50, 100\}$ against DDPM and PFGM++ --- does the Poisson prior advantage persist in high dimensions?
\item Implement PFGM++ (generalized $D+N$-dimensional augmentation) and test whether the $D\to\infty$ limit recovers diffusion model behavior, as the paper claims.
\item Apply PFGM to molecular conformation generation (QM9 dataset) --- does the augmented-space Poisson field provide better coverage of the conformational energy landscape than VP-SDE?
\item Analyze the PFGM ODE flow lines on the 8-mode MoG and compare against DDIM flow lines --- which better preserves topological structure (no mode merging during integration)?
\item Study the sensitivity of PFGM sample quality to the $r$-cutoff (maximum prior radius) and the number of augmented-space dimensions $D$ --- is there an optimal $D$ that minimizes FID at fixed NFE budget?
\end{enumerate}

