\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{tabularx}

\title{Replication Study of OSTI 2469515:\\
``Supervised Extraction of Near-Complete Genomes from Multiple Metagenomes''}
\author{Ollie (OpenClaw subagent) for Rick Stevens}
\date{2026-04-24}

\begin{document}
\maketitle

\begin{abstract}
We attempt a partial replication of Parrello \emph{et al.} (2021, OSTI 2469515), which
describes PATRIC's reference-guided (``supervised'') metagenome binning pipeline based
on \texttt{pheS} anchors, discriminating protein 12-mers, and \texttt{EvalG}/\texttt{EvalCon}
quality scoring. The authors' pipeline relies on the proprietary SEEDtk framework and
the 193,980-genome PATRIC/BV-BRC reference database, neither of which is practical to
install or stage on a single 10-core iMac in a 2.5 hour window. We therefore replicate
the paper's \textbf{baseline comparator} (MetaBAT2 on a SPAdes co-assembly with per-sample
coverage from minimap2/samtools) on a controlled synthetic 5-species metagenome generated
with InSilicoSeq. Because ground truth is known, we score completeness and contamination
directly by aligning each bin's contigs to the source reference genomes. All five
expected genomes are recovered as 100\%-pure bins with 85.6--98.3\% completeness, and
all five pass the MIMAG high-quality threshold (completeness $\geq 80\%$, contamination
$\leq 10\%$). This is consistent with the paper's observation that MetaBAT2 performs
well when differential coverage information across samples is available, and it
demonstrates that the non-supervised comparator recovers the ``easy'' portion of the
bin yield with near-perfect precision on clean synthetic data. The paper's core claim
--- that reference-guided binning \emph{exceeds} MetaBAT2 on complex real human-gut
samples (205 vs. 180 HQ bins across 23 ERR/SRR samples) --- cannot be replicated here
without SEEDtk/PATRIC and is documented as out-of-scope.
\end{abstract}

\section{Paper Summary (Claims Relevant to Replication)}

\begin{itemize}
  \item \textbf{Method:} Reference-guided binning. \texttt{pheS} (phenylalanyl-tRNA
  synthetase $\alpha$) sequences on assembled contigs are BLASTed against PATRIC.
  Each pheS-bearing contig $\geq 400$\,bp with $\geq 4\times$ coverage seeds a bin;
  contigs are then assigned based on sharing $\geq 10$ \emph{discriminating protein
  12-mers} with the bin's reference. Unbinned contigs are rescued via $\geq 50$\,bp
  exact DNA matches.
  \item \textbf{Quality scoring:} \texttt{EvalG} (completeness/contamination,
  CheckM-like) and \texttt{EvalCon} (fine consistency via random-forest predictors
  over $\sim$1{,}300 reliably predictable gene roles, $>93\%$ accuracy).
  \item \textbf{HQ threshold:} contamination $\leq 10\%$, fine consistency $\geq 87\%$,
  completeness $\geq 80\%$, exactly one pheS of valid length.
  \item \textbf{Benchmark:} 23 human metagenomic samples from Pasolli 2019.
  \begin{itemize}
    \item PATRIC supervised: 205 good / 164 poor bins
    \item MetaBAT2 + Bowtie2:  180 good / 660 poor bins
    \item MetaBAT2 (contigs only): 122 good / 431 poor bins
  \end{itemize}
  \item \textbf{Postprocessing finding:} Contamination-driven role filtering
  raised the average HQ bins/sample from 1.7 to 8.17.
  \item \textbf{pheS--genome similarity Pearson $r = 0.97$}; no HQ bins retrieved
  when best reference pheS similarity drops below 0.3.
\end{itemize}

\section{What We Replicated vs. Skipped}

\begin{tabularx}{\linewidth}{lX}
\toprule
\textbf{Component} & \textbf{Disposition} \\
\midrule
Read simulation            & \textbf{Replicated} with InSilicoSeq (HiSeq error model). \\
Co-assembly                & \textbf{Replicated} with metaSPAdes 4.2.0. \\
Per-sample mapping         & \textbf{Replicated} with minimap2 \texttt{sr} preset + samtools. \\
Baseline binning (MetaBAT2) & \textbf{Replicated.} \\
Ground-truth quality scoring & \textbf{Done directly} via minimap2 \texttt{asm5}
alignment of bin contigs to reference genomes (stronger than CheckM because we have
the exact sources). \\
CheckM/CheckM2             & Skipped: osx-64 install friction; not needed given
ground truth. Equivalent MIMAG thresholds applied. \\
PATRIC supervised pipeline (SEEDtk) & \textbf{Out of scope:} requires the
193{,}980-genome PATRIC database, RASTtk, EvalG, EvalCon, and SEEDtk --- not
installable on macOS in the time budget without cloud/BV-BRC access. \\
pheS anchoring / discriminating 12-mers & Not reimplemented; comparator only. \\
Real human-gut benchmark (23 Pasolli samples) & \textbf{Substituted} with a
5-species synthetic community ($\sim$1\,GB reads) to fit compute budget. \\
\bottomrule
\end{tabularx}

\section{Methods}

\subsection{Synthetic Community}
Five diverse bacterial reference genomes were downloaded from NCBI RefSeq
(\emph{Escherichia coli} K-12 MG1655, \emph{Staphylococcus aureus} NCTC 8325,
\emph{Bacillus subtilis} 168, \emph{Lactobacillus gasseri} ATCC 33323,
\emph{Porphyromonas gingivalis} ATCC 33277; total $\approx$15.9\,Mb). Contig
headers were rewritten with a species prefix for ground truth tracking.

Two metagenomic ``samples'' of $10^6$ read pairs (2$\times$126 bp) each were
generated with InSilicoSeq 2.0.1 (\texttt{HiSeq} error model, 8 CPUs) with
deliberately skewed and \emph{opposite} abundance vectors:

\begin{center}
\begin{tabular}{lrr}
\toprule
Species & Sample1 & Sample2 \\
\midrule
\emph{E. coli}         & 0.50 & 0.10 \\
\emph{S. aureus}       & 0.05 & 0.40 \\
\emph{B. subtilis}     & 0.25 & 0.10 \\
\emph{L. gasseri}      & 0.10 & 0.30 \\
\emph{P. gingivalis}   & 0.10 & 0.10 \\
\bottomrule
\end{tabular}
\end{center}

This differential-abundance design is what allows MetaBAT2's tetranucleotide
plus coverage signal to separate species cleanly.

\subsection{Pipeline}

\begin{enumerate}
  \item \textbf{Co-assembly:} metaSPAdes 4.2.0, \texttt{--meta --only-assembler},
  on the concatenated PE library (both samples). Output filtered to contigs
  $\geq 1000$\,bp.
  \item \textbf{Mapping:} minimap2 2.30 \texttt{-ax sr} per sample, piped to
  \texttt{samtools sort}. $>98.7\%$ reads-well-mapped per sample.
  \item \textbf{Coverage:} \texttt{jgi\_summarize\_bam\_contig\_depths} across
  both BAMs.
  \item \textbf{Binning:} MetaBAT2 2.18, \texttt{-m 1500 --seed 42}.
  \item \textbf{Evaluation:} Each bin's contigs aligned to the combined
  reference with minimap2 \texttt{-x asm5}. Each query contig is assigned to
  the species with the most matching bases; per-species totals give purity
  (contamination = $1 - $ purity), and completeness is the ratio of assigned
  bases to that species' genome length.
\end{enumerate}

Software note: megahit 1.2.9 from bioconda segfaulted on this Intel iMac (both
the \texttt{count} and \texttt{assemble} sub-steps with SIGSEGV irrespective of
BMI2 core selection); we switched to metaSPAdes, which ran to completion.

\section{Results}

metaSPAdes produced 659 contigs totaling 15.58\,Mb; 258 contigs $\geq 1000$\,bp
(15.53\,Mb) were fed to MetaBAT2. MetaBAT2 produced \textbf{5 bins} containing
98.00\% of the large-contig bases (15.21\,Mb). Per-bin evaluation against the
ground truth:

\begin{center}
\begin{tabular}{llrrrrc}
\toprule
Bin & Species & Purity \% & Complete \% & Bin size (bp) & Aligned (bp) & MIMAG HQ? \\
\midrule
bin.1 & \emph{P. gingivalis} & 100.00 & 85.64 & 2,021,268 & 2,016,788 & \checkmark \\
bin.2 & \emph{E. coli}       & 100.00 & 97.19 & 4,513,831 & 4,511,214 & \checkmark \\
bin.3 & \emph{S. aureus}     & 100.00 & 98.30 & 2,775,039 & 2,773,263 & \checkmark \\
bin.4 & \emph{L. gasseri}    & 100.00 & 95.51 & 1,809,639 & 1,809,248 & \checkmark \\
bin.5 & \emph{B. subtilis}   & 100.00 & 96.93 & 4,090,423 & 4,086,144 & \checkmark \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Headline numbers.}
\begin{itemize}
  \item 5 / 5 genomes recovered.
  \item Contamination: $0\%$ in every bin (every mapped base in every bin
        originated from that bin's main species).
  \item Completeness range: 85.6\%--98.3\%; mean 94.7\%.
  \item HQ bins (MIMAG $\geq 80\%$ / $\leq 10\%$): \textbf{5/5}.
  \item Paper's HQ threshold (EvalG $\geq 80\%$ complete, $\leq 10\%$ contam): all
        5 would qualify; the \texttt{EvalCon} fine-consistency criterion cannot
        be checked without RASTtk.
\end{itemize}

\section{Comparison With the Paper}

\begin{tabular}{lrrrr}
\toprule
Method & Samples & HQ bins & HQ/sample & Total bins \\
\midrule
PATRIC supervised (paper)    & 23 & 205 & 8.91 & 370 \\
MetaBAT2 + Bowtie2 (paper)   & 23 & 180 & 7.83 & 840 \\
MetaBAT2, contigs only (paper) & 23 & 122 & 5.30 & 553 \\
\midrule
\textbf{This work} (MetaBAT2, synthetic) & 1 & 5 & 5.00 & 5 \\
\bottomrule
\end{tabular}

Our per-sample HQ yield (5) is \emph{at the low end} of the paper's MetaBAT2
numbers only because our synthetic community contains only 5 species --- the
pipeline recovered \emph{all} of them. The paper's samples are real Pasolli
human gut metagenomes, in which hundreds of species compete, only a fraction
are assembleable from $\sim 10^7$ reads, and MetaBAT2 produces 840 total bins
of which only 180 are HQ (21.4\% good-bin rate). Our good-bin rate is 100\%
because there are no low-abundance under-assembled species to over-fragment.

\section{What Was and Was Not Reproduced}

\paragraph{Reproduced qualitatively.}
\begin{itemize}
  \item MetaBAT2 is capable of producing high-quality bins when differential
  coverage is informative (confirmed: 5/5 pure HQ bins from 2 samples with
  opposite abundance vectors).
  \item The general recipe (read simulate $\to$ co-assemble $\to$ map per
  sample $\to$ jgi depth $\to$ MetaBAT2) works end-to-end on a commodity Mac.
\end{itemize}

\paragraph{Not reproduced (honest accounting).}
\begin{itemize}
  \item The paper's central contribution --- \emph{supervised} binning via
  pheS + discriminating 12-mers against PATRIC --- was \emph{not implemented}.
  The SEEDtk stack requires a custom RASTtk / SEED / EvalCon install and the
  full PATRIC genome corpus; this is BV-BRC-hosted and not trivially
  reproducible off-platform.
  \item The paper's head-to-head superiority of PATRIC over MetaBAT2 on real
  human-gut data was not directly tested; we only reproduced the
  comparator arm.
  \item Postprocessing's claimed boost from 1.7 to 8.17 HQ bins/sample
  (a $4.8\times$ improvement attributable specifically to EvalCon-driven role
  filtering) is inaccessible without EvalCon.
  \item The pheS-similarity / HQ-yield monotone relationship (Table 2 of the
  paper) is not testable without a reference pheS database and BLAST against
  PATRIC.
\end{itemize}

\section{Self-Rated Replication Score}

\textbf{4/10.} We reproduced the comparator baseline end-to-end and verified it
works correctly on controlled data, but we did not reproduce the paper's
actual supervised method or the human-gut benchmark it was measured on. A
fairer 8+/10 would require either BV-BRC platform access or a substantial
($\gg$2.5\,h) re-implementation of SEEDtk against a staged PATRIC snapshot.

\section{Reproducibility Bundle}

All files are under
\texttt{\textasciitilde/Dropbox/REPLICATE-PROJECT/2469515-Supervised-extraction-of-near-complete-genomes-from/replication/}:

\begin{itemize}
  \item \texttt{data/} --- reference genomes, abundance files, simulated reads
  \item \texttt{assembly/spades/} --- metaSPAdes output; \texttt{contigs.fa} (filtered)
  \item \texttt{bins/sample\{1,2\}.bam, depth.txt} --- alignments and coverage
  \item \texttt{bins/metabat/bin.\{1..5\}.fa} --- final MAGs
  \item \texttt{checkm/bin\_eval.tsv} --- ground-truth completeness/purity table
  \item \texttt{report/report.pdf} --- this document
\end{itemize}

\paragraph{Environment.}
conda env \texttt{metabin}: metaSPAdes 4.2.0, minimap2 2.30, samtools 1.23.1,
metabat2 2.18, seqkit, InSilicoSeq 2.0.1, biopython 1.87, Python 3.13.
Host: CherryRd, macOS, 20 CPU / 128\,GB RAM.

\end{document}
